### 2014-03-07 paper/paper.tex
Add paper stuff into git

\documentclass[titlepage]{article}
\usepackage{graphicx}       % include figures
\usepackage{float}          % align figures
\usepackage{amsmath}        % \pm
% \usepackage{indentfirst}
\usepackage{achemso}
\usepackage[bf]{caption}    % bold figure names
\usepackage{url}
\usepackage{setspace}
\restylefloat{table}        % same page tables
\usepackage{chngpage}
\usepackage{multirow}

\begin{document}

\title{Application of Machine Learning Methods to the Optoelectronic properties of Benzobisazoles}
\author{Christopher Collins}

\maketitle

\doublespace
\section{Introduction}

Organic solar cell stuff, cruiform stuff, machine learning stuff

\section{Naming Scheme}

The naming scheme is broken down into three separate components. These parts are the core, the sides, and the options.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=1.25in]{TXY.png}
  \end{center}
  \caption{TXY Core}
  \label{fig:txy}
\end{figure}

The core is the central part of the molecule. All cores are identified by a combination of three letters. The first letter indicates whether or not the structure is Cis or Trans which correspond to the letters C and T respectively. The second letter in the core name is the symbol for the element that is in the core without the $\pi$ bond (meh?) (for consistency in naming this will always be the top right atom). This can be one of O, S, N, P, or C. The final letter is the remaining element's symbol which can be N, P, or C (for consistency this will always be the bottom right atom).

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=1.25in]{CXY.png}
  \end{center}
  \caption{CXY Core}
  \label{fig:cxy}
\end{figure}

The sides of the name are split into three groups based on the location in the structure. Going from the core orientation, these three groups are the left, center, and right sides. The left and right sides of the structure form the horizontal axis. The center group is the vertical axis and ... something about how they are the same....

\begin{table}[H]
  \centering
  \caption{Aryl Groups}
  \begin{tabular}{ccc}
    Label   & Name          & Structure \\
    \hline
    2       & Double Bond   &           \\
    3       & Triple Bond   &           \\
    4       & Phenyl        &           \\
    5       & Thiophene     &           \\
    6       & Pyridine      &           \\
    7       & Carbazole     &           \\
    8       & TZ            &           \\
    9       & EDOT          &           \\
    \hline
  \end{tabular}
  \label{tab:aryl}
\end{table}

Each side is then broken down into components of Aryl, X, and R groups. Aryl groups are indicated by the numbers 2 through 9 as seen in Table \ref{tab:aryl}. Aryl groups form the main chain part of the structure...

\begin{table}[H]
  \centering
  \caption{X/R-Groups}
  \begin{tabular}{ccc}
    Label   & Name          & Structure \\
    \hline
    A/a     & Hydrogen  &           \\
    B/b     & Chlorine  &           \\
    C/c     & Bromine   &           \\
    D/d     & CN        &           \\
    E/e     & CCH       &           \\
    F/f     & OH        &           \\
    G/g     & SH        &           \\
    H/h     & $NH_2$    &           \\
    I/i     & $CH_3$    &           \\
    J/j     & Phenyl    &           \\
    K/k     & TMS       &           \\
    L/l     & $OCH_3$   &           \\
    *       & Spacer    &           \\
    \hline
  \end{tabular}
  \label{tab:xrgroups}
\end{table}

X and R groups are both composed of the same set of substituents seen in TABLE 2. X groups are the letters A through L, and r groups are a through l. The main difference between X and R groups is where they are placed in the chain, whereas R-Groups are placed on the Aryl group that directly proceeds them. As can be seen in TABLE 1 R-groups come in pairs of two. These groups can either be the same or different(?). Because there are some Aryl groups that do not allow any R-groups there is an additional spacer R-group that is designated as *. It has no effect on the structure of the molecule, it is just used as a place holder when converting the names to a feature vector.

Starting from the core going outward, side chains take two main forms. They are either an X-group (which terminates the entire side) or they are a triplet of an Aryl group and two R-groups. If it is an aryl group triplet, then the process can continue.
(X-group|[Aryl, R-group, R-group])

The final component of the naming scheme is a set of options. These are broken up into two main classes. The first pair of options are the polymer options and they indicate how many times the molecules is repeated along the horizontal (n) axis (chain?) or the vertical (m) axis (chain?). The second set of options is a set of x, y, and z that are the number of times that the molecule is stacked in each direction(?).

Structures were picked using this naming scheme to try to cover as many combinations of cores, sides, and options.

\section{Feature Vectors}

Using this naming scheme, it is apparent that there are multiple ways that these could be converted into feature vectors for use in machine learning.

\subsection{Naive}
The first, and most simplistic, is to take all the possible options ....
The problem with this approach is that is the size of the feature vector groups proportional to the length of the longest side chain. Another problem with this type of feature vector it does not exploit similarities in the structure. (one might expect a chlorine two steps away from the core to cause about the same effect as one one step away times some decay factor).

\subsection{Decay}
To counter act these problems a second feature vector was created that used a decay function \eqref{decay}. $A$, $H$, and $p$ are arbitrary constants used to adjust the decay. By grouping similar components together (?), it normalizes implict features by ... something (charge, hammet parameters).

\begin{equation}\label{decay}
    Value = \sum_i^n (A d_i^{-H})^{p}
\end{equation}

The bad thing about this kind of decay function is that it is not separable if $H \times p \le 1$. This would mean that there is no unique conversion between a given feature vector and its associated name/structure.

\subsection{Decay with Length Corrections}

One problem with the first decay type feature vector is it makes the assumption that all the distances between are the same length. Since the effects of atoms are highly dependent on distance this sort of assumption is problematic for heterogeneous side groups. \eqref{decay2} Something something. This normalizes all the lengths such that longer structures will increase the distance more than shorter structures.

$\vec L$ is a vector of the length from the first primary connector to the second for all the Aryl groups. Using this vector, a ratio matrix is constructed such that $R_{ij} = \vec L_j / \vec L_i$. By doing this, all the lengths are normalized relative ??.
$$\textbf{R} = \vec L / \vec L^{T}$$
$$ \vec d = \sum_{i,j}^n \textbf{R}_{ij}  $$
\begin{equation}\label{decay2}
    Value = \sum_i^n (A d_i^{-H})^{p}
\end{equation}

The problem with this feature vector is that it is not separable.

\subsection{Decay with Predictions}

In attempt to exploit the relation between HOMO, LUMO, and Band Gap, another feature vector was constructed. The feature vector was composed of a combination of the decay vector plus the addition of the two properties that were not being trained for.

$$ predictedHOMO = predict(Decay, HOMO) $$
$$ predictedLUMO = predict(Decay, LUMO) $$
$$ predictedGAP = predict(Decay, GAP) $$
$$ GAPit = [Decay, predictedHOMO, predictedLUMO] $$
$$ HOMOit = [Decay, predictedLUMO, predictedGAP] $$
$$ LUMOit = [Decay, predictedGAP, predictedHOMO] $$

\section{Methods}
\subsection{Mean Value}
\subsection{Linear Regression}
\subsubsection{Regular}
\subsubsection{Ridged}
\subsection{Tree}
\subsection{k-Nearest Neighbors}
\subsection{Support Vector Machines}

% \begin{figure}[H]
%   \begin{center}
%     \includegraphics[width=5in]{scan2.png}
%   \end{center}
%   \caption{Scan of SVM parameters C and gamma}
%   \label{fig:homolumo}
% \end{figure}

\subsubsection{Gaussian Kernel}
$$ k(x, x') = exp\left( −\frac{1}{2\sigma^2} \lVert x - x'  \rVert^2 \right) $$

\subsubsection{Laplacian Kernel}
$$ k(x, x') = exp\left( −\frac{1}{\sigma} \lvert x - x' \rvert \right) $$

\section{Procedure}

Roughly 1100 benzobisazole structures were built (using a script?). Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31(g). After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31(g).

Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison (?).

Once all the calculations were completed, the resulting log files were parsed for HOMO, LUMO, and Band Gap values. From there, the first three feature vectors were constructed (Naive, Decay, Decay with Distance Correction) and the resulting vectors were stored with the parsed log data.

(When to mention Decay with Prediction creation?)

Once all the data and feature vectors were collected, the machine learning stuff...

For each feature vector, property, method set the methods relevant parameters were optimized (C, gamma, max depth, alpha, n neighbors). Then using these optimized parameters, the machine learning models were trained using k-folds specifically using 10 folds (bla bla).

(maybe invert the procedure)

\section{Results}

\begin{table}[H]
  \centering
  \caption{Band Gap Results}
  \begin{tabular}{lll}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive}     & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2628 $\pm$ 0.019 \\
                               & Linear Ridge & 0.2571 $\pm$ 0.020 \\
                               & Tree         & 0.1429 $\pm$ 0.016 \\
                               & k-NN         & 0.2096 $\pm$ 0.018 \\
                               & SVM Gauss    & \textbf{0.1355 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1681 $\pm$ 0.013 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2531 $\pm$ 0.022 \\
                               & Linear Ridge & 0.2506 $\pm$ 0.023 \\
                               & Tree         & 0.1318 $\pm$ 0.018 \\
                               & k-NN         & 0.2112 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.1297 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1591 $\pm$ 0.011 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2485 $\pm$ 0.020 \\
                               & Linear Ridge & 0.2466 $\pm$ 0.020 \\
                               & Tree         & 0.1492 $\pm$ 0.029 \\
                               & k-NN         & 0.2169 $\pm$ 0.013 \\
                               & SVM Gauss    & \textbf{0.1314 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1631 $\pm$ 0.011 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.1211 $\pm$ 0.011 \\
                               & Linear Ridge & 0.1174 $\pm$ 0.010 \\
                               & Tree         & 0.1369 $\pm$ 0.012 \\
                               & k-NN         & 0.1724 $\pm$ 0.015 \\
                               & SVM Gauss    & \textbf{0.1004 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1154 $\pm$ 0.009 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

% dummy           0.5051634571 $\pm$ 0.0445987177
% linear          0.2628013865 $\pm$ 0.0191410131
% linear ridge    0.2571941447 $\pm$ 0.0201764172
% tree            0.1429020978 $\pm$ 0.0167680834
% neighbors       0.2096637025 $\pm$ 0.0181147991
% svm gauss       0.1355760073 $\pm$ 0.0119249721
% svm laplace     0.1681324515 $\pm$ 0.0130277607

% dummy           0.5051634571 $\pm$ 0.0445987177
% linear          0.2531408695 $\pm$ 0.0224904198
% linear ridge    0.2506620918 $\pm$ 0.0231378900
% tree            0.1318830228 $\pm$ 0.0188910719
% neighbors       0.2112675515 $\pm$ 0.0170114767
% svm gauss       0.1297476028 $\pm$ 0.0110853891
% svm laplace     0.1591951178 $\pm$ 0.0113296220

% dummy           0.5051634571 $\pm$ 0.0445987177
% linear          0.2485031607 $\pm$ 0.0200054080
% linear ridge    0.2466766131 $\pm$ 0.0209252773
% tree            0.1492425133 $\pm$ 0.0293509142
% neighbors       0.2169500774 $\pm$ 0.0136509896
% svm gauss       0.1314727141 $\pm$ 0.0116959757
% svm laplace     0.1631757401 $\pm$ 0.0117913187

% dummy           0.5051634571 $\pm$ 0.0445987177
% linear          0.1211359604 $\pm$ 0.0116286996
% linear ridge    0.1174973321 $\pm$ 0.0101995097
% tree            0.1369228897 $\pm$ 0.0123968003
% neighbors       0.1724752783 $\pm$ 0.0152423160
% svm gauss       0.1004123381 $\pm$ 0.0106025428
% svm laplace     0.1154254876 $\pm$ 0.0096740880

\begin{table}[H]
  \centering
  \caption{HOMO Results}
  \begin{tabular}{lll}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.2002 $\pm$ 0.024 \\
                               & Linear Ridge & 0.1949 $\pm$ 0.024 \\
                               & Tree         & 0.1546 $\pm$ 0.012 \\
                               & k-NN         & 0.2449 $\pm$ 0.025 \\
                               & SVM Gauss    & \textbf{0.1126 $\pm$ 0.014} \\
                               & SVM Laplace  & 0.1557 $\pm$ 0.016 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.1868 $\pm$ 0.025 \\
                               & Linear Ridge & 0.1860 $\pm$ 0.025 \\
                               & Tree         & 0.1455 $\pm$ 0.017 \\
                               & k-NN         & 0.2549 $\pm$ 0.026 \\
                               & SVM Gauss    & \textbf{0.1069 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1431 $\pm$ 0.014 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.1883 $\pm$ 0.024 \\
                               & Linear Ridge & 0.1875 $\pm$ 0.025 \\
                               & Tree         & 0.1453 $\pm$ 0.021 \\
                               & k-NN         & 0.2622 $\pm$ 0.028 \\
                               & SVM Gauss    & \textbf{0.1082 $\pm$ 0.012} \\
                               & SVM Laplace  & 0.1457 $\pm$ 0.017 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.0904 $\pm$ 0.007 \\
                               & Linear Ridge & 0.0897 $\pm$ 0.008 \\
                               & Tree         & 0.1439 $\pm$ 0.016 \\
                               & k-NN         & 0.1734 $\pm$ 0.020 \\
                               & SVM Gauss    & \textbf{0.0852 $\pm$ 0.007} \\
                               & SVM Laplace  & 0.1001 $\pm$ 0.008 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

% dummy            0.4330672042 $\pm$ 0.0380947474
% linear           0.2002858544 $\pm$ 0.0244903400
% linear ridge     0.1949752271 $\pm$ 0.0248602704
% tree             0.1546552205 $\pm$ 0.0122826022
% neighbors        0.2449855565 $\pm$ 0.0258103540
% svm gauss        0.1126612407 $\pm$ 0.0141583310
% svm laplace      0.1557953600 $\pm$ 0.0169683266

% dummy            0.4330672042 $\pm$ 0.0380947474
% linear           0.1868573168 $\pm$ 0.0252679509
% linear ridge     0.1860609806 $\pm$ 0.0257993800
% tree             0.1455811816 $\pm$ 0.0175405978
% neighbors        0.2549135699 $\pm$ 0.0261735083
% svm gauss        0.1069055686 $\pm$ 0.0100414699
% svm laplace      0.1431763121 $\pm$ 0.0145504211

% dummy            0.4330672042 $\pm$ 0.0380947474
% linear           0.1883473946 $\pm$ 0.0248143868
% linear ridge     0.1875977704 $\pm$ 0.0251635444
% tree             0.1453857318 $\pm$ 0.0214142873
% neighbors        0.2622268718 $\pm$ 0.0287591181
% svm gauss        0.1082111822 $\pm$ 0.0124536000
% svm laplace      0.1457133829 $\pm$ 0.0170146564

% dummy            0.4330672042 $\pm$ 0.0380947474
% linear           0.0904848003 $\pm$ 0.0077179117
% linear ridge     0.0897196018 $\pm$ 0.0085006159
% tree             0.1439614181 $\pm$ 0.0167746654
% neighbors        0.1734307394 $\pm$ 0.0202218099
% svm gauss        0.0852044604 $\pm$ 0.0072159851
% svm laplace      0.1001281598 $\pm$ 0.0086522943

\begin{table}[H]
  \centering
  \caption{LUMO Results}
  \begin{tabular}{lll}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1900 $\pm$ 0.028 \\
                               & Linear Ridge & 0.1862 $\pm$ 0.025 \\
                               & Tree         & 0.1529 $\pm$ 0.007 \\
                               & k-NN         & 0.2351 $\pm$ 0.019 \\
                               & SVM Gauss    & \textbf{0.1055 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1454 $\pm$ 0.014 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1816 $\pm$ 0.026 \\
                               & Linear Ridge & 0.1801 $\pm$ 0.026 \\
                               & Tree         & 0.1510 $\pm$ 0.024 \\
                               & k-NN         & 0.2323 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.1022 $\pm$ 0.015} \\
                               & SVM Laplace  & 0.1317 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1847 $\pm$ 0.027 \\
                               & Linear Ridge & 0.1828 $\pm$ 0.027 \\
                               & Tree         & 0.1540 $\pm$ 0.023 \\
                               & k-NN         & 0.2348 $\pm$ 0.014 \\
                               & SVM Gauss    & \textbf{0.1029 $\pm$ 0.012} \\
                               & SVM Laplace  & 0.1331 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1233 $\pm$ 0.012 \\
                               & Linear Ridge & 0.0877 $\pm$ 0.011 \\
                               & Tree         & 0.0863 $\pm$ 0.010 \\
                               & k-NN         & 0.1699 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.0792 $\pm$ 0.009} \\
                               & SVM Laplace  & 0.0922 $\pm$ 0.009 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

% dummy           0.4475990362 $\pm$ 0.0379190939
% linear          0.1900266591 $\pm$ 0.0285711677
% linear ridge    0.1862466873 $\pm$ 0.0252330179
% tree            0.1529660715 $\pm$ 0.0077728697
% neighbors       0.2351363937 $\pm$ 0.0193158199
% svm gauss       0.1055791858 $\pm$ 0.0104366108
% svm laplace     0.1454523271 $\pm$ 0.0145551515

% dummy           0.4475990362 $\pm$ 0.0379190939
% linear          0.1816689922 $\pm$ 0.0263603308
% linear ridge    0.1801892946 $\pm$ 0.0269365682
% tree            0.1510884685 $\pm$ 0.0242985650
% neighbors       0.2323162704 $\pm$ 0.0179171316
% svm gauss       0.1022628994 $\pm$ 0.0150820066
% svm laplace     0.1317870230 $\pm$ 0.0121778503

% dummy           0.4475990362 $\pm$ 0.0379190939
% linear          0.1847361405 $\pm$ 0.0279060679
% linear ridge    0.1828131087 $\pm$ 0.0270449435
% tree            0.1540660334 $\pm$ 0.0230038065
% neighbors       0.2348623132 $\pm$ 0.0142070847
% svm gauss       0.1029487972 $\pm$ 0.0123167244
% svm laplace     0.1331720123 $\pm$ 0.0123964303

% dummy           0.4475990362 $\pm$ 0.0379190939
% tree            0.1233738710 $\pm$ 0.0122788181
% linear          0.0877481316 $\pm$ 0.0110845291
% linear ridge    0.0863736416 $\pm$ 0.0108794424
% neighbors       0.1699337745 $\pm$ 0.0170310968
% svm gauss       0.0792332669 $\pm$ 0.0091141118
% svm laplace     0.0922304705 $\pm$ 0.0092304161

\section{Conclusions}

BLOB
Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors. The optimized paramters for the ... $C \approx 10$ and $\gamma \approx 0.05$.

For the feature vectors, the decay was the best performaing feature vector with the parameters $A = 1, H = 1, p = 1$. (0.71) As well as having a better overall performance, it is also much faster than the naive feature vector because it has fewer components. This increased speed could especially be seen when training the data.
With the addition of predicted HOMO/LUMO values for the decay feature vector, the performance for estimating the goal features increased by about 25\%.

Unexpectedly, the decay function with distance corrections did not perform any better than the regular decay feature vector. In theory, this should have worked better with hetrogenous side chains...

There were a few anomalies in the results. The most noticeable is long tail distribution of errors ...
several molecules with unusually high errors ($8A\_TON\_A\_A$), structures where features overlap ($A\_TON\_4ed\_A$)

None of the feature vectors take into account the kuhn expression for polymer chains. This leads to high errors as n or m > 1. The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay (?).

%        Neural Network
%            Tested various network configurations and could the best MAE was around 0.20 eV
%            Network configuration seemed to have minimal impact on results
%            Problem attributed to inexperience with Neural Networks

\nocite{ruddigkeit_enumeration_2012}
\nocite{darley_beyond_2008}
\nocite{frisch_gaussian_2009}
\nocite{montavon_machine_2013}
\nocite{handley_dynamically_2009}
\nocite{hansen_assessment_2013}
\nocite{schutt_how_2013}
\nocite{reymond_exploring_2012}
\nocite{whitfield_computational_2013}
\nocite{hansen_assessment_2013-1}
\nocite{ra_dft_2008}
\nocite{martell_assessment_1997}
\nocite{montavon_learning_2012}
\nocite{domingos_few_2012}
\nocite{martin_benchmark_1997}
\nocite{handley_potential_2010}
\nocite{rupp_fast_2012}

\bibliography{paper}
\newpage
\appendix

\end{document}

### 2014-03-08 ml/clfs.py
Start reformatting run.py into separate files

@@ -1,0 +1,101 @@
+import numpy
+
+from sklearn import svm
+
+from pybrain.datasets import SupervisedDataSet
+from pybrain.supervised.trainers import BackpropTrainer
+from pybrain.structure import FeedForwardNetwork
+from pybrain.structure import LinearLayer, SigmoidLayer
+from pybrain.structure import FullConnection
+
+from utils import gauss_kernel_gen, laplace_kernel_gen
+
+class Linear(object):
+    def __init__(self):
+        self.weights = None
+
+    def fit(self, X, y):
+        X = numpy.matrix(X)
+        y = numpy.matrix(y).T
+        self.weights = numpy.linalg.pinv(X.T*X)*X.T*y
+
+    def predict(self, X):
+        X = numpy.matrix(X)
+        return X*self.weights
+
+class KernelRegression(object):
+    def __init__(self, kernel=None, gamma=0.05, C=10):
+        self.weights = None
+        self.kernel = gauss_kernel_gen(gamma)
+        self.X = None
+        self.C = C
+        self.gamma = gamma
+    def fit(self, X, y):
+        X = numpy.matrix(X)
+        y = numpy.matrix(y).T
+        self.X = X
+        print self.kernel(X, X).shape, (self.C*numpy.eye(X.shape[0])).shape
+        self.weights = numpy.linalg.pinv(self.kernel(X, X)+self.C*numpy.eye(X.shape[0]))*y
+    def predict(self, X):
+        X = numpy.matrix(X)
+        return self.kernel(X, self.X)*self.weights
+
+
+class NeuralNet(object):
+    def __init__(self, hidden_layers=None):
+        self.hidden_layers = list(hidden_layers)
+
+    def build_network(self, layers=None):
+        layerobjects = []
+        for item in layers:
+            try:
+                t, n = item
+                if t == "sig":
+                    if n == 0:
+                        continue
+                    layerobjects.append(SigmoidLayer(n))
+            except TypeError:
+                layerobjects.append(LinearLayer(item))
+
+        n = FeedForwardNetwork()
+        n.addInputModule(layerobjects[0])
+
+        for i, layer in enumerate(layerobjects[1:-1]):
+            n.addModule(layer)
+            connection = FullConnection(layerobjects[i], layerobjects[i+1])
+            n.addConnection(connection)
+
+        n.addOutputModule(layerobjects[-1])
[…]

### 2014-03-08 ml/display.py

@@ -1,0 +1,170 @@
+import numpy
+import matplotlib.pyplot as plt
+
+from sklearn import decomposition
+from sklearn import dummy
+from sklearn import neighbors
+from sklearn import cross_validation
+from sklearn.metrics import r2_score
+
+from utils import scan
+
+
+def sort_xset(xset):
+    temp = {}
+    for yset in xset:
+        for name in yset:
+            zipped = zip(*yset[name][:-1])
+            (_, test) = zipped[0]
+            if temp.get(name):
+                temp[name].append(test[0])
+            else:
+                temp[name] = [test[0]]
+    for key, val in temp.items():
+        temp[key] = sum(val)/len(val)
+    return [y for y in sorted(temp, key=lambda x: temp[x])]
+
+
+def display_sorted_results(results):
+    clfs = []
+    for xset in results:
+        order = sort_xset(xset)
+        for name in order:
+            print '"' + name + '"',
+            lines = []
+            for yset in xset:
+                clfs.append(yset[name][-1])
+                for i, (train, test) in enumerate(zip(*yset[name][:-1])):
+                    try:
+                        lines[i].extend([train, test])
+                    except IndexError:
+                        lines.append([train, test])
+            for line in lines:
+                tests = line[1::2]
+                means = [x[0] for x in tests]
+                stds = [x[1] for x in tests]
+                means.append(sum(means)/len(means))
+                stds.append(sum(stds)/len(stds))
+                spacers = ['', '', '', '']
+                print ','.join(str(x) for x in sum(zip(spacers, means, stds), ()))
+        print '\n'
+    return clfs
+
+
+def PCA_stuff(X, y, title="Principal Component Analysis"):
+    pca = decomposition.PCA(n_components=2)
+    pca.fit(X)
+    print pca.explained_variance_ratio_, sum(pca.explained_variance_ratio_)
+    temper = pca.transform(X)
+    Xs = temper[:,0]
+    Ys = temper[:,1]
+    COLOR = (y-y.min())/y.max()
[…]

### 2014-03-08 ml/ml.py

@@ -1,0 +1,147 @@
+import csv
+import multiprocessing
+import ast
+import cPickle
+
+import numpy
+from sklearn import decomposition
+from sklearn import linear_model
+from sklearn import svm
+from sklearn import tree
+from sklearn import dummy
+from sklearn import neighbors
+
+from display import display_sorted_results, plot_scan_2d, plot_scan, PCA_stuff
+from display import plot_num_samples
+from utils import OptimizedCLF
+
+
+data = []
+with open("data_clean.csv", "r") as csvfile:
+    reader = csv.reader(csvfile, delimiter=',', quotechar='"')
+    for row in reader:
+        temp = [row[3]]
+        for item in row[4:]:
+            try:
+                x = ast.literal_eval(item)
+                if x == []:
+                    break
+                temp.append(x)
+            except:
+                pass
+
+        if len(temp) == 9:
+            data.append(temp)
+
+M = len(data)
+
+HOMO = numpy.zeros((M, 1))
+LUMO = numpy.zeros((M, 1))
+DIPOLE = numpy.zeros((M, 1))
+ENERGY = numpy.zeros((M, 1))
+GAP = numpy.zeros((M, 1))
+TIME = numpy.zeros((M, 1))
+
+features = []
+for i, (name, feat, occ, virt, orb, dip, eng, gap, time) in enumerate(data):
+    features.append(feat)
+    HOMO[i] = occ
+    LUMO[i] = virt
+    DIPOLE[i] = dip
+    ENERGY[i] = eng
+    GAP[i] = gap
+    TIME[i] = time
+
+FEATURES = []
+for group in zip(*tuple(features)):
+    FEATURES.append(numpy.matrix(group))
+
+
+def test_sklearn(X, y):
+    funcs = {
+        "dummy": (dummy.DummyRegressor, dict()),
+        "linear": (Linear, dict()),
+        "linear ridge": (linear_model.Ridge, {"alpha": 0.5}),
+        "neighbors": (neighbors.KNeighborsRegressor, {"n_neighbors": [2, 3, 5, 10]}),
+        "svm gauss": (svm.SVR, {"C": 10, "gamma": 0.05}),
+        "svm laplace": (SVMLaplace, {"C": 10, "gamma": 0.05}),
+        "tree": (tree.DecisionTreeRegressor, {"max_depth": [1, 5, 10, 50, None]}),
[…]

### 2014-03-08 ml/neural.py

@@ -1,0 +1,28 @@
+clf = NeuralNet([("sig", 250), ("sig", 250)])
+print test_clf(FEATURES[0], GAP, clf, num=1)
+
+layers = []
+from itertools import product
+vals = [0, 10, 50, 100, 200, 400]
+possible_layers = set(tuple(x for x in vals if x) for vals in product(vals, vals, vals, vals))
+print len(possible_layers)
+
+def func(layers):
+    print layers
+    new = zip(["sig"]*len(layers), layers)
+    clf = NeuralNet(new)
+    res = test_clf(FEATURES[0], GAP, clf, num=1)
+    print res
+    return res
+
+def func(num): return test_clf(FEATURES[0], GAP, NeuralNet([("sig", x)]), num=1)[1][0]
+
+
+pool = multiprocessing.Pool(processes=4)
+results = pool.map(func, possible_layers)
+
+for i, layers in enumerate(possible_layers):
+    new = zip(["sig"]*len(layers), layers)
+    clf = NeuralNet(new)
+    print i, layers,
+    print test_clf(FEATURES[0], GAP, clf, num=1)

### 2014-03-08 ml/utils.py

@@ -1,0 +1,123 @@
+import itertools
+
+import numpy
+import scipy.optimize
+from scipy.spatial.distance import cdist
+from sklearn import cross_validation
+from sklearn.metrics import mean_absolute_error
+
+
+def test_clf(X, y, clf, test_size=0.2, num=20):
+    ylist = y.T.tolist()[0]
+    train = numpy.zeros(num)
+    cross = numpy.zeros(num)
+    for i in xrange(num):
+        X_train, X_test, y_train, y_test = cross_validation.train_test_split(X, ylist, test_size=test_size)
+        clf.fit(X_train, y_train)
+        train[i] = mean_absolute_error(clf.predict(X_train), y_train)
+        cross[i] = mean_absolute_error(clf.predict(X_test), y_test)
+    return (train.mean(), train.std()), (cross.mean(), cross.std())
+
+
+def test_clf_kfold(X, y, clf, folds=10):
+    train = numpy.zeros(folds)
+    cross = numpy.zeros(folds)
+    for i, (train_idx, test_idx) in enumerate(cross_validation.KFold(y.shape[0], n_folds=folds)):
+        X_train = X[train_idx]
+        X_test = X[test_idx]
+        y_train = y[train_idx].T.tolist()[0]
+        y_test = y[test_idx].T.tolist()[0]
+        clf.fit(X_train, y_train)
+        train[i] = mean_absolute_error(clf.predict(X_train), y_train)
+        cross[i] = mean_absolute_error(clf.predict(X_test), y_test)
+    return (train.mean(), train.std()), (cross.mean(), cross.std())
+
+
+def get_high_errors(errors, limit=1.5):
+    aerrors = numpy.abs(errors)
+    mean = aerrors.mean()
+    std = aerrors.std()
+    results = []
+    for x in aerrors.argsort(0)[::-1]:
+        if aerrors[x[0,0]] > (mean + limit * std):
+            results.append((data[x[0,0]][0], aerrors[x[0,0]][0,0]))
+    return results
+
+def scan(X, y, function, params):
+    size = [len(x) for x in params.values()]
+    train_results = numpy.zeros(size)
+    test_results = numpy.zeros(size)
+    keys = params.keys()
+    values = params.values()
+    for group in itertools.product(*values):
+        idx = tuple([a.index(b) for a,b in zip(values, group) if len(a) > 1])
+        a = dict(zip(keys, group))
+        clf = function(**a)
[…]

### 2014-03-08 run.py

@@ -1,588 +1,1 @@
-import csv
-import itertools
-import multiprocessing
-import ast
-import cPickle
-
-import numpy
-import matplotlib.pyplot as plt
-from scipy.spatial.distance import cdist
-import scipy.optimize
-
-from sklearn import decomposition
-from sklearn import linear_model
-from sklearn import svm
-from sklearn import tree
-from sklearn import dummy
-from sklearn import neighbors
-from sklearn import cross_validation
-from sklearn.metrics import mean_absolute_error, r2_score
-
-from pybrain.tools.shortcuts import buildNetwork
-from pybrain.datasets import SupervisedDataSet
-from pybrain.supervised.trainers import BackpropTrainer
-from pybrain.structure import FeedForwardNetwork
-from pybrain.structure import LinearLayer, SigmoidLayer
-from pybrain.structure import FullConnection
-
-
-###############################################################################
-# Load Data
-###############################################################################
-
-
-data = []
-with open("data_clean.csv", "r") as csvfile:
-    reader = csv.reader(csvfile, delimiter=',', quotechar='"')
-    for row in reader:
-        temp = [row[3]]
-        for item in row[4:]:
-            try:
-                x = ast.literal_eval(item)
-                if x == []:
-                    break
-                temp.append(x)
-            except:
-                pass
-
-        if len(temp) == 9:
-            data.append(temp)
-
-M = len(data)
-
-HOMO = numpy.zeros((M, 1))
-LUMO = numpy.zeros((M, 1))
-DIPOLE = numpy.zeros((M, 1))
-ENERGY = numpy.zeros((M, 1))
-GAP = numpy.zeros((M, 1))
-TIME = numpy.zeros((M, 1))
-
-features = []
-for i, (name, feat, occ, virt, orb, dip, eng, gap, time) in enumerate(data):
-    features.append(feat)
-    HOMO[i] = occ
-    LUMO[i] = virt
-    DIPOLE[i] = dip
-    ENERGY[i] = eng
-    GAP[i] = gap
-    TIME[i] = time
-
-FEATURES = []
-for group in zip(*tuple(features)):
-    FEATURES.append(numpy.matrix(group))
-
-
-
-###############################################################################
-# CLFs
-###############################################################################
-
-
-class Linear(object):
-    def __init__(self):
-        self.weights = None
-
-    def fit(self, X, y):
-        X = numpy.matrix(X)
-        y = numpy.matrix(y).T
[…]

### 2014-03-08 ml/ml.py
Rearrange positioning in files to fix multiprocessing

@@ -1,6 +1,4 @@
-import csv
 import multiprocessing
-import ast
 import cPickle
 
 import numpy
@@ -11,50 +9,10 @@ from sklearn import tree
 from sklearn import dummy
 from sklearn import neighbors
 
+from clfs import Linear, SVMLaplace
 from display import display_sorted_results, plot_scan_2d, plot_scan, PCA_stuff
 from display import plot_num_samples
-from utils import OptimizedCLF
-
-
-data = []
-with open("data_clean.csv", "r") as csvfile:
-    reader = csv.reader(csvfile, delimiter=',', quotechar='"')
-    for row in reader:
-        temp = [row[3]]
-        for item in row[4:]:
-            try:
-                x = ast.literal_eval(item)
-                if x == []:
-                    break
-                temp.append(x)
-            except:
-                pass
-
-        if len(temp) == 9:
-            data.append(temp)
-
-M = len(data)
-
-HOMO = numpy.zeros((M, 1))
-LUMO = numpy.zeros((M, 1))
-DIPOLE = numpy.zeros((M, 1))
-ENERGY = numpy.zeros((M, 1))
-GAP = numpy.zeros((M, 1))
-TIME = numpy.zeros((M, 1))
-
-features = []
-for i, (name, feat, occ, virt, orb, dip, eng, gap, time) in enumerate(data):
-    features.append(feat)
-    HOMO[i] = occ
-    LUMO[i] = virt
-    DIPOLE[i] = dip
-    ENERGY[i] = eng
-    GAP[i] = gap
-    TIME[i] = time
-
-FEATURES = []
-for group in zip(*tuple(features)):
-    FEATURES.append(numpy.matrix(group))
+from utils import OptimizedCLF, test_clf_kfold
 
 
 def test_sklearn(X, y):
@@ -83,65 +41,61 @@ def test_sklearn(X, y):
     return results
 
 
-def multi_func(xset):
+def get_extended_features(homo, lumo, gap, features):
+    try:
+        with open("features1.pkl", "rb") as f:
+            extended_features = cPickle.load(f)
+        if len(extended_features) == 4 * len(features):
+            return extended_features
+    except IOError:
+        pass
+
+    extended_features = []
+    for i, feat in enumerate(features):
[…]

### 2014-03-08 run.py

@@ -1,1 +1,59 @@
+import csv
+import ast
+import cPickle
+
+import numpy
+
 import ml.ml
+
+
+data = []
+with open("data_clean.csv", "r") as csvfile:
+    reader = csv.reader(csvfile, delimiter=',', quotechar='"')
+    for row in reader:
+        temp = [row[3]]
+        for item in row[4:]:
+            try:
+                x = ast.literal_eval(item)
+                if x == []:
+                    break
+                temp.append(x)
+            except:
+                pass
+
+        if len(temp) == 9:
+            data.append(temp)
+
+M = len(data)
+
+HOMO = numpy.zeros((M, 1))
+LUMO = numpy.zeros((M, 1))
+DIPOLE = numpy.zeros((M, 1))
+ENERGY = numpy.zeros((M, 1))
+GAP = numpy.zeros((M, 1))
+TIME = numpy.zeros((M, 1))
+
+features = []
+for i, (name, feat, occ, virt, orb, dip, eng, gap, time) in enumerate(data):
+    features.append(feat)
+    HOMO[i] = occ
+    LUMO[i] = virt
+    DIPOLE[i] = dip
+    ENERGY[i] = eng
+    GAP[i] = gap
+    TIME[i] = time
+
+FEATURES = []
+for group in zip(*tuple(features)):
+    FEATURES.append(numpy.matrix(group))
+FEATURES1 = ml.ml.get_extended_features(HOMO, LUMO, GAP, FEATURES[1:])
+
+
+results, results2, clfs, clfs2 = ml.ml.main((HOMO, ), FEATURES, FEATURES1)
+
+if __name__ == "__main__":
+    print time.time() - start
+    plot_scan_2d(FEATURES[1], GAP, svm.SVR, {"C": [0.05, 0.1, 0.5, 1, 5, 10, 50, 100, 500, 1000], "gamma": [0.0001, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]})
+    plot_scan(FEATURES[1], GAP, linear_model.Ridge, {"alpha": [0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]})
+    PCA_stuff(FEATURES[1], GAP)
+    plot_num_samples(FEATURES[1], GAP, svm.SVR(C=10, gamma=0.05))

### 2014-03-08 run.py
Fix time imports

@@ -1,6 +1,7 @@
 import csv
 import ast
 import cPickle
+import time
 
 import numpy
 
@@ -34,14 +35,14 @@ GAP = numpy.zeros((M, 1))
 TIME = numpy.zeros((M, 1))
 
 features = []
-for i, (name, feat, occ, virt, orb, dip, eng, gap, time) in enumerate(data):
+for i, (name, feat, occ, virt, orb, dip, eng, gap, t) in enumerate(data):
     features.append(feat)
     HOMO[i] = occ
     LUMO[i] = virt
     DIPOLE[i] = dip
     ENERGY[i] = eng
     GAP[i] = gap
-    TIME[i] = time
+    TIME[i] = t
 
 FEATURES = []
 for group in zip(*tuple(features)):
@@ -50,6 +51,7 @@ FEATURES1 = ml.ml.get_extended_features(HOMO, LUMO, GAP, FEATURES[1:])
 
 
 results, results2, clfs, clfs2 = ml.ml.main((HOMO, ), FEATURES, FEATURES1)
+start = time.time()
 
 if __name__ == "__main__":
     print time.time() - start

### 2014-03-08 run.py
Fix remaining imports in run.py

@@ -4,8 +4,11 @@ import cPickle
 import time
 
 import numpy
+from sklearn import svm
+from sklearn import linear_model
 
 import ml.ml
+from ml.display import plot_scan_2d, plot_scan, PCA_stuff, plot_num_samples
 
 
 data = []

### 2014-03-08 ml/display.py
Fix imports in ml.display

@@ -7,7 +7,7 @@ from sklearn import neighbors
 from sklearn import cross_validation
 from sklearn.metrics import r2_score
 
-from utils import scan
+from utils import scan, test_clf
 
 
 def sort_xset(xset):

### 2014-03-08 ml/display.py
Return X, Y, and color values from PCA_stuff

@@ -66,6 +66,7 @@ def PCA_stuff(X, y, title="Principal Component Analysis"):
     plt.ylabel("PCA 2")
     plt.show()
     plt.clf()
+    return Xs, Ys, COLOR
 
 
 def PCA_stuff_3d(X, y, title="Principal Component Analysis"):

### 2014-03-08 ml/display.py
Add ability to plot a scan surface

@@ -169,3 +169,21 @@ def plot_actual_prediction(actual, prediction, label=""):
     plt.title("%s Actual verses Prediction" % label)
     plt.legend(loc="best")
     plt.show()
+
+def plot_scan_2d_surface(X, y, function, params):
+    listform = params.items()
+    train, test = scan(X, y, function, params)
+    surface(test)
+    return train, test
+
+
+def surface(data, colormap="jet"):
+    fig = plt.figure()
+    ax = fig.gca(projection='3d')
+    X = numpy.arange(data.shape[0])
+    Y = numpy.arange(data.shape[1])
+    XX, YY = numpy.meshgrid(X, Y)
+    surf = ax.plot_surface(XX, YY, data, rstride=1, cstride=1, cmap=colormap, linewidth=0, antialiased=False, shade=True)
+    ax.set_zlim(data.min(), data.max())
+    fig.colorbar(surf, shrink=0.5, aspect=5)
+    plt.show()

### 2014-03-09 ml/display.py
Add function to display the background after using PCA

@@ -1,4 +1,5 @@
 import numpy
+from mpl_toolkits.mplot3d import Axes3D
 import matplotlib.pyplot as plt
 
 from sklearn import decomposition
@@ -67,6 +68,21 @@ def PCA_stuff(X, y, title="Principal Component Analysis"):
     plt.show()
     plt.clf()
     return Xs, Ys, COLOR
+
+
+def plot_PCA_backgroun(Xs, Ys, Zs, method='nearest'):
+    from scipy.interpolate import griddata
+    xgrid = numpy.linspace(Xs.min(), Xs.max(), 1000)
+    ygrid = numpy.linspace(Ys.min(), Ys.max(), 1000)
+    XX, YY = numpy.meshgrid(xgrid, ygrid)
+    points = numpy.concatenate([numpy.matrix(Xs).T, numpy.matrix(Ys).T], 1)
+    grid_z2 = griddata(points, Zs, (XX, YY), method=method)
+    plt.imshow(grid_z2.T, extent=(0,1,0,1), origin='lower')
+    # cm = plt.get_cmap("HOT")
+    # X = (Xs-Xs.min())/(Xs.max()-Xs.min())
+    # Y = (Ys-Ys.min())/(Ys.max()-Ys.min())
+    # plt.scatter(X, Y, c=Zs,s=80, marker='o', edgecolors='none')
+    plt.show()
 
 
 def PCA_stuff_3d(X, y, title="Principal Component Analysis"):
@@ -169,6 +185,7 @@ def plot_actual_prediction(actual, prediction, label=""):
     plt.title("%s Actual verses Prediction" % label)
     plt.legend(loc="best")
     plt.show()
+
 
 def plot_scan_2d_surface(X, y, function, params):
     listform = params.items()

### 2014-03-11 build_data.sh
Change data file names

@@ -1,7 +1,7 @@
 #!/bin/sh
 
 fileparser=~/projects/chemtools-webapp/chemtools/fileparser.py
-data=/home/chris/research/ML/logs
+data=logs
 
 echo "Parsing Generated"
 python $fileparser -f $data/sets/ > data.csv

### 2014-03-11 clean_data.py

@@ -1,7 +1,7 @@
 import csv
 
 names = dict()
-with open("data.csv", "r") as csvfile, open("data_clean.csv", "w") as csvcleanfile:
+with open("data.csv", "r") as csvfile, open("cleaned_data.csv", "w") as csvcleanfile:
     reader = csv.reader(csvfile, delimiter=',', quotechar='"')
     writer = csv.writer(csvcleanfile, delimiter=',', quotechar='"')
     for row in reader:

### 2014-03-11 run.py

@@ -12,7 +12,7 @@ from ml.display import plot_scan_2d, plot_scan, PCA_stuff, plot_num_samples
 
 
 data = []
-with open("data_clean.csv", "r") as csvfile:
+with open("cleaned_data.csv", "r") as csvfile:
     reader = csv.reader(csvfile, delimiter=',', quotechar='"')
     for row in reader:
         temp = [row[3]]

### 2014-03-11 run.py
Group all the goal values together into a tuple

@@ -46,6 +46,7 @@ for i, (name, feat, occ, virt, orb, dip, eng, gap, t) in enumerate(data):
     ENERGY[i] = eng
     GAP[i] = gap
     TIME[i] = t
+YSETS = (HOMO, LUMO, GAP)
 
 FEATURES = []
 for group in zip(*tuple(features)):
@@ -53,7 +54,7 @@ for group in zip(*tuple(features)):
 FEATURES1 = ml.ml.get_extended_features(HOMO, LUMO, GAP, FEATURES[1:])
 
 
-results, results2, clfs, clfs2 = ml.ml.main((HOMO, ), FEATURES, FEATURES1)
+results, results2, clfs, clfs2 = ml.ml.main(YSETS, FEATURES, FEATURES1)
 start = time.time()
 
 if __name__ == "__main__":

### 2014-03-11 run.py
Remove time from run.py

@@ -1,7 +1,6 @@
 import csv
 import ast
 import cPickle
-import time
 
 import numpy
 from sklearn import svm
@@ -38,14 +37,14 @@ GAP = numpy.zeros((M, 1))
 TIME = numpy.zeros((M, 1))
 
 features = []
-for i, (name, feat, occ, virt, orb, dip, eng, gap, t) in enumerate(data):
+for i, (name, feat, occ, virt, orb, dip, eng, gap, time) in enumerate(data):
     features.append(feat)
     HOMO[i] = occ
     LUMO[i] = virt
     DIPOLE[i] = dip
     ENERGY[i] = eng
     GAP[i] = gap
-    TIME[i] = t
+    TIME[i] = time
 YSETS = (HOMO, LUMO, GAP)
 
 FEATURES = []
@@ -55,10 +54,8 @@ FEATURES1 = ml.ml.get_extended_features(HOMO, LUMO, GAP, FEATURES[1:])
 
 
 results, results2, clfs, clfs2 = ml.ml.main(YSETS, FEATURES, FEATURES1)
-start = time.time()
 
 if __name__ == "__main__":
-    print time.time() - start
     plot_scan_2d(FEATURES[1], GAP, svm.SVR, {"C": [0.05, 0.1, 0.5, 1, 5, 10, 50, 100, 500, 1000], "gamma": [0.0001, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]})
     plot_scan(FEATURES[1], GAP, linear_model.Ridge, {"alpha": [0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]})
     PCA_stuff(FEATURES[1], GAP)

### 2014-03-11 ml/display.py
Fix typo

@@ -70,7 +70,7 @@ def PCA_stuff(X, y, title="Principal Component Analysis"):
     return Xs, Ys, COLOR
 
 
-def plot_PCA_backgroun(Xs, Ys, Zs, method='nearest'):
+def plot_PCA_background(Xs, Ys, Zs, method='nearest'):
     from scipy.interpolate import griddata
     xgrid = numpy.linspace(Xs.min(), Xs.max(), 1000)
     ygrid = numpy.linspace(Ys.min(), Ys.max(), 1000)

### 2014-03-11 run.py
Cleanup exmaple plot code

@@ -7,8 +7,8 @@ from sklearn import svm
 from sklearn import linear_model
 
 import ml.ml
-from ml.display import plot_scan_2d, plot_scan, PCA_stuff, plot_num_samples
-
+from ml.display import plot_scan_2d, plot_scan, plot_num_samples
+from ml.display import PCA_stuff, plot_PCA_background
 
 data = []
 with open("cleaned_data.csv", "r") as csvfile:
@@ -56,7 +56,14 @@ FEATURES1 = ml.ml.get_extended_features(HOMO, LUMO, GAP, FEATURES[1:])
 results, results2, clfs, clfs2 = ml.ml.main(YSETS, FEATURES, FEATURES1)
 
 if __name__ == "__main__":
-    plot_scan_2d(FEATURES[1], GAP, svm.SVR, {"C": [0.05, 0.1, 0.5, 1, 5, 10, 50, 100, 500, 1000], "gamma": [0.0001, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]})
-    plot_scan(FEATURES[1], GAP, linear_model.Ridge, {"alpha": [0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]})
-    PCA_stuff(FEATURES[1], GAP)
+    # Make some example plots
+    2d_scan_params = {
+        "C": [0.05, 0.1, 0.5, 1, 5, 10, 50, 100, 500, 1000],
+        "gamma": [0.0001, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]
+    }
+    plot_scan_2d(FEATURES[1], GAP, svm.SVR, 2d_scan_params)
+    scan_params = {"alpha": [0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]}
+    plot_scan(FEATURES[1], GAP, linear_model.Ridge, scan_params)
+    Xs, Ys, Zs = PCA_stuff(FEATURES[1], GAP)
+    plot_PCA_background(Xs, Ys, Zs)
     plot_num_samples(FEATURES[1], GAP, svm.SVR(C=10, gamma=0.05))

### 2014-03-11 run.py
Move all of run.py into the __main__ block

@@ -10,52 +10,52 @@ import ml.ml
 from ml.display import plot_scan_2d, plot_scan, plot_num_samples
 from ml.display import PCA_stuff, plot_PCA_background
 
-data = []
-with open("cleaned_data.csv", "r") as csvfile:
-    reader = csv.reader(csvfile, delimiter=',', quotechar='"')
-    for row in reader:
-        temp = [row[3]]
-        for item in row[4:]:
-            try:
-                x = ast.literal_eval(item)
-                if x == []:
-                    break
-                temp.append(x)
-            except:
-                pass
-
-        if len(temp) == 9:
-            data.append(temp)
-
-M = len(data)
-
-HOMO = numpy.zeros((M, 1))
-LUMO = numpy.zeros((M, 1))
-DIPOLE = numpy.zeros((M, 1))
-ENERGY = numpy.zeros((M, 1))
-GAP = numpy.zeros((M, 1))
-TIME = numpy.zeros((M, 1))
-
-features = []
-for i, (name, feat, occ, virt, orb, dip, eng, gap, time) in enumerate(data):
-    features.append(feat)
-    HOMO[i] = occ
-    LUMO[i] = virt
-    DIPOLE[i] = dip
-    ENERGY[i] = eng
-    GAP[i] = gap
-    TIME[i] = time
-YSETS = (HOMO, LUMO, GAP)
-
-FEATURES = []
-for group in zip(*tuple(features)):
-    FEATURES.append(numpy.matrix(group))
-FEATURES1 = ml.ml.get_extended_features(HOMO, LUMO, GAP, FEATURES[1:])
-
-
-results, results2, clfs, clfs2 = ml.ml.main(YSETS, FEATURES, FEATURES1)
 
 if __name__ == "__main__":
+    data = []
+    with open("cleaned_data.csv", "r") as csvfile:
+        reader = csv.reader(csvfile, delimiter=',', quotechar='"')
+        for row in reader:
+            temp = [row[3]]
+            for item in row[4:]:
+                try:
+                    x = ast.literal_eval(item)
+                    if x == []:
+                        break
+                    temp.append(x)
+                except:
+                    pass
+
+            if len(temp) == 9:
+                data.append(temp)
+
+    M = len(data)
+
+    HOMO = numpy.zeros((M, 1))
[…]

### 2014-03-12 run.py
Fix typo

@@ -57,11 +57,11 @@ if __name__ == "__main__":
     results, results2, clfs, clfs2 = ml.ml.main(YSETS, FEATURES, FEATURES1)
 
     # Make some example plots
-    2d_scan_params = {
+    scan_2d_params = {
         "C": [0.05, 0.1, 0.5, 1, 5, 10, 50, 100, 500, 1000],
         "gamma": [0.0001, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]
     }
-    plot_scan_2d(FEATURES[1], GAP, svm.SVR, 2d_scan_params)
+    plot_scan_2d(FEATURES[1], GAP, svm.SVR, scan_2d_params)
     scan_params = {"alpha": [0.005, 0.01, 0.05, 0.1, 0.5, 1, 5]}
     plot_scan(FEATURES[1], GAP, linear_model.Ridge, scan_params)
     Xs, Ys, Zs = PCA_stuff(FEATURES[1], GAP)

### 2014-03-12 ml/display.py
Fix array dimensions in plot_PCA_background

@@ -76,7 +76,7 @@ def plot_PCA_background(Xs, Ys, Zs, method='nearest'):
     ygrid = numpy.linspace(Ys.min(), Ys.max(), 1000)
     XX, YY = numpy.meshgrid(xgrid, ygrid)
     points = numpy.concatenate([numpy.matrix(Xs).T, numpy.matrix(Ys).T], 1)
-    grid_z2 = griddata(points, Zs, (XX, YY), method=method)
+    grid_z2 = griddata(points, Zs, (XX, YY), method=method)[:,:,0]
     plt.imshow(grid_z2.T, extent=(0,1,0,1), origin='lower')
     # cm = plt.get_cmap("HOT")
     # X = (Xs-Xs.min())/(Xs.max()-Xs.min())

### 2014-03-12 ml/display.py
Move scipy import to top of file

@@ -1,4 +1,5 @@
 import numpy
+from scipy.interpolate import griddata
 from mpl_toolkits.mplot3d import Axes3D
 import matplotlib.pyplot as plt
 
@@ -71,7 +72,6 @@ def PCA_stuff(X, y, title="Principal Component Analysis"):
 
 
 def plot_PCA_background(Xs, Ys, Zs, method='nearest'):
-    from scipy.interpolate import griddata
     xgrid = numpy.linspace(Xs.min(), Xs.max(), 1000)
     ygrid = numpy.linspace(Ys.min(), Ys.max(), 1000)
     XX, YY = numpy.meshgrid(xgrid, ygrid)

### 2014-06-06 paper/paper.tex
Change paper to use eps images instead of png
Update paper

@@
-\documentclass[titlepage]{article}
+% \documentclass[10pt,twocolumn]{article}
+\documentclass[10pt]{article}
 \usepackage{graphicx}       % include figures
@@
 \usepackage{multirow}
+% \graphicspath{ {./figures/} }
 
@@
 
-\title{Application of Machine Learning Methods to the Optoelectronic properties of Benzobisazoles}
+\title{Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles}
 \author{Christopher Collins}
@@
 
-\doublespace
+\begin{abstract}
+By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively.
+These results also come with the added benefit of being 30,000,000 times faster than the equivilant Density Functional Theory calculation.
+\end{abstract}
+
+% \doublespace
 \section{Introduction}
 
-Organic solar cell stuff, cruiform stuff, machine learning stuff
+There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor effeciency [CITE]. Computational
+
+Because of these problems, there is a need to rapidly predict the properties of molecules so that.
+Machine learning has been shown to be a fast way to predict properties of many systems and specifically, has been shown to be a viable way to predict properties of molecules\cite{hansen_assessment_2013} \cite{montavon_machine_2013}.
+
+For this study, we will be looking at using different machine learning methods in conjunction with Density Functional Theory calculations to be able to predict the
 
@@
 
+To be able to represent these molecular structures to the machine learning algorthims, a common naming scheme was formed such that it could be reaily converted into a vector form.
+This naming scheme exploits the planar nature of benzobisazoles as well as their cruxiformic structure.
 The naming scheme is broken down into three separate components. These parts are the core, the sides, and the options.
@@
   \begin{center}
-    \includegraphics[width=1.25in]{TXY.png}
+    \includegraphics[width=1.25in]{figures/TXY.png}
   \end{center}
@@
 The second letter in the core name is the symbol for the element that is in the core without the $\pi$ bond (meh?) (for consistency in naming this will always be the top right atom).
-This can be one of O, S, N, P, or C.
+This can be one of Oxygen (O), Sulfur (S), Nitrogen (N), Phosporous (P), or Carbon (C).
 The final letter is the remaining element's symbol which can be N, P, or C (for consistency this will always be the bottom right atom).
@@
   \begin{center}
-    \includegraphics[width=1.25in]{CXY.png}
+    \includegraphics[width=1.25in]{figures/CXY.png}
   \end{center}
@@
 
+\begin{figure}[H]
+  \begin{center}
+    \includegraphics[width=1.75in]{figures/aryl.png}
+  \end{center}
+  \caption{Aryl Groups}
+\end{figure}
+
 \begin{table}[H]
@@
   \caption{Aryl Groups}
-  \begin{tabular}{ccc}
-    Label   & Name          & Structure \\
+  \begin{tabular}{lc}
+    Label   & Name                    \\
     \hline
-    2       & Double Bond   &           \\
-    3       & Triple Bond   &           \\
-    4       & Phenyl        &           \\
-    5       & Thiophene     &           \\
-    6       & Pyridine      &           \\
-    7       & Carbazole     &           \\
-    8       & TZ            &           \\
-    9       & EDOT          &           \\
+    2       & Double Bond             \\
+    3       & Triple Bond             \\
+    4       & Phenyl                  \\
+    5       & Thiophene               \\
+    6       & Pyridine                \\
+    7       & Carbazole               \\
+    8       & Tetrazine               \\
+    9       & Ethylenedioxythiophene  \\
     \hline
@@
   \caption{X/R-Groups}
-  \begin{tabular}{ccc}
-    Label   & Name          & Structure \\
+  \begin{tabular}{lc}
+    Label   & Name      \\
     \hline
-    A/a     & Hydrogen  &           \\
-    B/b     & Chlorine  &           \\
-    C/c     & Bromine   &           \\
-    D/d     & CN        &           \\
-    E/e     & CCH       &           \\
-    F/f     & OH        &           \\
-    G/g     & SH        &           \\
-    H/h     & $NH_2$    &           \\
-    I/i     & $CH_3$    &           \\
-    J/j     & Phenyl    &           \\
-    K/k     & TMS       &           \\
-    L/l     & $OCH_3$   &           \\
-    *       & Spacer    &           \\
+    A/a     & Hydrogen  \\
+    B/b     & Chlorine  \\
+    C/c     & Bromine   \\
+    D/d     & CN        \\
+    E/e     & CCH       \\
+    F/f     & OH        \\
+    G/g     & SH        \\
+    H/h     & $NH_2$    \\
+    I/i     & $CH_3$    \\
+    J/j     & Phenyl    \\
+    K/k     & TMS       \\
+    L/l     & $OCH_3$   \\
+    *       & Spacer    \\
     \hline
@@
 \section{Feature Vectors}
+
+To be able to represent these structures to the computer, and consequently to the machine learning algorthms they must be vectorized.
 
@@
 
-\section{Methods}
-\subsection{Mean Value}
-\subsection{Linear Regression}
-\subsubsection{Regular}
-\subsubsection{Ridged}
-\subsection{Tree}
-\subsection{k-Nearest Neighbors}
-\subsection{Support Vector Machines}
+\section{Machine Learning Methods}
 
-% \begin{figure}[H]
-%   \begin{center}
-%     \includegraphics[width=5in]{scan2.png}
-%   \end{center}
-%   \caption{Scan of SVM parameters C and gamma}
-%   \label{fig:homolumo}
-% \end{figure}
+In previous work \cite{montavon_machine_2013}, it has been shown that different machine learning algorthms have had drastically different performance when used to predict molecular properties.
+Because of this, seven algorthms were picked to compare.
+These were mean value, linear regression, linear ridged regression, tree regression, k-nearest neighbors, and support vector machines.
+The mean value method is used as a baseline for all of the other methods.
+()
 
-\subsubsection{Gaussian Kernel}
-$$ k(x, x') = exp\left( −\frac{1}{2\sigma^2} \lVert x - x'  \rVert^2 \right) $$
-
-\subsubsection{Laplacian Kernel}
-$$ k(x, x') = exp\left( −\frac{1}{\sigma} \lvert x - x' \rvert \right) $$
+ \begin{figure}[H]
+   \begin{center}
+     \includegraphics[width=5in]{figures/surf.png}
+   \end{center}
+   \caption{Scan of SVM parameters C and $\gamma$}
+   \label{fig:scan}
+ \end{figure}
 
@@
 
-Roughly 1100 benzobisazole structures were built (using a script?).
-Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31(g).
-After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31(g).
+Roughly 1100 benzobisazole structures were built.
+Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*.
+After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*.
 
@@
 
-(When to mention Decay with Prediction creation?)
-
-Once all the data and feature vectors were collected, the machine learning stuff...
-
-For each feature vector, property, method set the methods relevant parameters were optimized (C, gamma, max depth, alpha, n neighbors).
-Then using these optimized parameters, the machine learning models were trained using k-folds specifically using 10 folds (bla bla).
-
-(maybe invert the procedure)
+Once all the data and feature vectors were collected, they were feed into the machine learning algorthms.
+For each feature vector, property, method set the methods relevant parameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors).
+Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds.
+All of the results were then tabled and compared based on their mean absolute errors (MAE).
 
@@
   \caption{Band Gap Results}
-  \begin{tabular}{lll}
+  \begin{tabular}{llr}
             Feature Vector     & Method       & MAE (eV)                \\
@@
 
+ \begin{figure}[H]
+   \begin{center}
+     \includegraphics[width=5in]{figures/gapbars.pdf}
+   \end{center}
+   \caption{Band Gap Results}
+   \label{fig:scan}
+ \end{figure}
+
 % dummy           0.5051634571 $\pm$ 0.0445987177
@@
   \caption{HOMO Results}
-  \begin{tabular}{lll}
+  \begin{tabular}{llr}
             Feature Vector     & Method       & MAE (eV)                \\
@@
   \end{tabular}
-  \label{tab:gapresults}
+  \label{tab:homoresults}
 \end{table}
+
+ \begin{figure}[H]
+   \begin{center}
+     \includegraphics[width=5in]{figures/homobars.pdf}
+   \end{center}
+   \caption{HOMO Results}
+   \label{fig:scan}
+ \end{figure}
 
@@
   \caption{LUMO Results}
-  \begin{tabular}{lll}
+  \begin{tabular}{llr}
             Feature Vector     & Method       & MAE (eV)                \\
@@
 
+ \begin{figure}[H]
+   \begin{center}
+     \includegraphics[width=5in]{figures/lumobars.pdf}
+   \end{center}
+   \caption{LUMO Results}
+   \label{fig:scan}
+ \end{figure}
+
 % dummy           0.4475990362 $\pm$ 0.0379190939
@@
 
-BLOB
 Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors.
-The optimized paramters for the ...
-$C \approx 10$ and $\gamma \approx 0.05$.
+The optimized paramters for the method were $C \approx 10$ and $\gamma \approx 0.05$.
 
@@
 
-Unexpectedly, the decay function with distance corrections did not perform any better than the regular decay feature vector. In theory, this should have worked better with hetrogenous side chains...
+Unexpectedly, the decay function with distance corrections did not perform any better than the regular decay feature vector.
+In theory, this should have worked better with hetrogenous side chains, but its use seemed to only increase the MAE.
 
@@
 
+To run the original DFT and TDDFT calculations for these moelcules took about 35,0000 CPU hours. Calculating the same properties using these machine learning methods took about 4 seconds.
+
+% In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions.
+Unfortunatly, the results were not satisfactory relative to the amount of time required (0.20 eV MAE).
+Drastic changes to the network made minimal differences to the final error.
+This is attirbuted to inexperience with proper methodologies with Neural Networks.
+
+\section{Future Work}
+
+Continue making tweaks to reduce error
+Collect more data
+
 None of the feature vectors take into account the kuhn expression for polymer chains.
@@
 The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay (?).
-
-%        Neural Network
-%            Tested various network configurations and could the best MAE was around 0.20 eV
-%            Network configuration seemed to have minimal impact on results
-%            Problem attributed to inexperience with Neural Networks
+Preliminary work with this addition corrected seems to be the best way to account for polymerization of benzobisazoles.
+Test with additional properties (total energy, dipole, etc.)
+Generalize for any structure
+Make it faster
+% In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions.
+Unfortunatly, the results were not satisfactory relative to the amount of time required (0.20 eV MAE).
+Drastic changes to the network made minimal differences to the final error.
+This is attirbuted to inexperience with proper methodologies with Neural Networks.
 

### 2014-06-06 paper/paper.tex
Continue to update the paper

@@
 By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively.
-These results also come with the added benefit of being 30,000,000 times faster than the equivilant Density Functional Theory calculation.
+These results also come with the added benefit of being 30,000,000 times faster than the equivalent Density Functional Theory calculation.
 \end{abstract}
 
-% \doublespace
+\doublespace
 \section{Introduction}
@@
 
-For this study, we will be looking at using different machine learning methods in conjunction with Density Functional Theory calculations to be able to predict the
+For this study, we will be looking at using different machine learning methods in conjunction with Density Functional Theory calculations to be able to predict the highest occupied molecular orbital (HOMO), lowest unoccupied molecular orbital (LUMO), and the band gap.
 
@@
 
-To be able to represent these molecular structures to the machine learning algorthims, a common naming scheme was formed such that it could be reaily converted into a vector form.
+To be able to represent these molecular structures to the machine learning algorithms, a common naming scheme was formed such that it could be readily converted into a vector form.
 This naming scheme exploits the planar nature of benzobisazoles as well as their cruxiformic structure.
@@
   \begin{center}
-    \includegraphics[width=1.25in]{figures/TXY.png}
+    \includegraphics[width=4in]{figures/cores.pdf}
   \end{center}
-  \caption{TXY Core}
-  \label{fig:txy}
+  \caption{TXY and CXY Cores}
+  \label{fig:cores}
 \end{figure}
 
-The core is the central part of the molecule.
+The core is the central three fused ring system of the benzobisazoles.
 All cores are identified by a combination of three letters.
 The first letter indicates whether or not the structure is Cis or Trans which correspond to the letters C and T respectively.
-The second letter in the core name is the symbol for the element that is in the core without the $\pi$ bond (meh?) (for consistency in naming this will always be the top right atom).
+The second letter in the core name is the symbol for the element that is in the core without the $\pi$ bond (for consistency in naming this will always be the top right atom).
 This can be one of Oxygen (O), Sulfur (S), Nitrogen (N), Phosporous (P), or Carbon (C).
 The final letter is the remaining element's symbol which can be N, P, or C (for consistency this will always be the bottom right atom).
-
-\begin{figure}[H]
-  \begin{center}
-    \includegraphics[width=1.25in]{figures/CXY.png}
-  \end{center}
-  \caption{CXY Core}
-  \label{fig:cxy}
-\end{figure}
 
@@
 The left and right sides of the structure form the horizontal axis.
-The center group is the vertical axis and ...
-something about how they are the same....
+The center group is the vertical axis.
+For simplicity, both of the groups along the vertical axis are the same chain as they emanate from the core.
 
@@
   \begin{center}
-    \includegraphics[width=1.75in]{figures/aryl.png}
+    \includegraphics[width=4in]{figures/aryl.pdf}
   \end{center}
@@
 
-Each side is then broken down into components of Aryl, X, and R groups.
+Each side is then broken down into components of Aryl, X groups, and R groups.
 Aryl groups are indicated by the numbers 2 through 9 as seen in Table \ref{tab:aryl}.
-Aryl groups form the main chain part of the structure...
+Aryl groups form the main chain part of the structure, they are able to extend the length of the chain and some have places for R groups (4, 5, 6, 7).
 
@@
 
-X and R groups are both composed of the same set of substituents seen in TABLE 2.
+X and R groups are both composed of the same set of substituents seen in Table \ref{tab:xrgroups}.
 X groups are the letters A through L, and r groups are a through l.
 The main difference between X and R groups is where they are placed in the chain, whereas R-Groups are placed on the Aryl group that directly proceeds them.
-As can be seen in TABLE 1 R-groups come in pairs of two.
+As can be seen in Table \ref{tab:aryl} R-groups come in pairs of two.
 These groups can either be the same or different(?).
@@
 If it is an aryl group triplet, then the process can continue.
-(X-group|[Aryl, R-group, R-group])
+(X-group $\vert$ [Aryl, R-group, R-group])
 
@@
 
-To be able to represent these structures to the computer, and consequently to the machine learning algorthms they must be vectorized.
+To be able to represent these structures to the computer, and consequently to the machine learning algorithms they must be vectorized.
 
@@
 \subsection{Naive}
-The first, and most simplistic, is to take all the possible options ....
+
+The first, and most simplistic, is to take all the possible combinations and create a binary vector from it with each 1 in a location representing a particular combination.
+From the regular structure of the benzobisazoles, this can be done at the aryl group triplet level.
 The problem with this approach is that is the size of the feature vector groups proportional to the length of the longest side chain.
@@
 $A$, $H$, and $p$ are arbitrary constants used to adjust the decay.
-By grouping similar components together (?), it normalizes implict features by ...
-something (charge, hammet parameters).
+By grouping similar components together, it normalizes implicit features (charge, Hammet parameters, and etc).
 
@@
 
-$\vec L$ is a vector of the length from the first primary connector to the second for all the Aryl groups.
-Using this vector, a ratio matrix is constructed such that $R_{ij} = \vec L_j / \vec L_i$.
-By doing this, all the lengths are normalized relative ??.
-$$\textbf{R} = \vec L / \vec L^{T}$$
-$$ \vec d = \sum_{i,j}^n \textbf{R}_{ij}  $$
+$M_i$ is a normalizing factor for each segment in the chain. By doing this, all the lengths are normalized relative to the first element.
+
 \begin{equation}\label{decay2}
-    Value = \sum_i^n (A d_i^{-H})^{p}
+    Value = \sum_i^n \left(A \left(\frac{d_i}{M_i}\right)^{-H} \right)^{p}
 \end{equation}
@@
 
-In attempt to exploit the relation between HOMO, LUMO, and Band Gap, another feature vector was constructed.
+In attempt to exploit the relation between HOMO, LUMO, and band gap, another feature vector was constructed.
 The feature vector was composed of a combination of the decay vector plus the addition of the two properties that were not being trained for.
+This was done in two stages, the first stage involved running the machine learning calculations as normal and then storing those results.
 
@@
 $$ predictedGAP = predict(Decay, GAP) $$
-$$ GAPit = [Decay, predictedHOMO, predictedLUMO] $$
-$$ HOMOit = [Decay, predictedLUMO, predictedGAP] $$
-$$ LUMOit = [Decay, predictedGAP, predictedHOMO] $$
+
+The second stage involved concatenating the original feature vectors to the vectors of predicted HOMO, LUMO, and band gap values.
+For each new feature vector, the goal property's respective predicted value was left out to avoid skewing the results.
+
+$$ newGAP = [Decay, predictedHOMO, predictedLUMO] $$
+$$ newHOMO = [Decay, predictedLUMO, predictedGAP] $$
+$$ newLUMO = [Decay, predictedGAP, predictedHOMO] $$
+
+These feature vectors were then feed back into the machine learning algorithms to get the final results.
+
+$$ finalHOMO = predict(Decay, newHOMO) $$
+$$ finalLUMO = predict(Decay, newLUMO) $$
+$$ finalGAP = predict(Decay, newGAP) $$
 
@@
 
-In previous work \cite{montavon_machine_2013}, it has been shown that different machine learning algorthms have had drastically different performance when used to predict molecular properties.
-Because of this, seven algorthms were picked to compare.
+In previous work \cite{montavon_machine_2013}, it has been shown that different machine learning algorithms have had drastically different performance when used to predict molecular properties.
+Because of this, seven algorithms were picked to compare.
 These were mean value, linear regression, linear ridged regression, tree regression, k-nearest neighbors, and support vector machines.
 The mean value method is used as a baseline for all of the other methods.
-()
 
@@
 After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*.
-
-Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison (?).
+Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.
 
@@
 Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds.
-All of the results were then tabled and compared based on their mean absolute errors (MAE).
+All of the results were then tabulated and compared based on their mean absolute errors (MAE) calculated as the distance the ML predicted value was from DFT calculated value.
+
+\section{Results}
+
+ \begin{figure}[H]
+   \begin{center}
+     \includegraphics[width=4.25in]{figures/gapbars.pdf}
+   \end{center}
+   % \caption{Band Gap Results}
+   \label{fig:scan}
+ \end{figure}
+
+ \begin{figure}[H]
+   \begin{center}
+     \includegraphics[width=4.25in]{figures/homobars.pdf}
+   \end{center}
+   % \caption{HOMO Results}
+   \label{fig:scan}
+ \end{figure}
+
+ \begin{figure}[H]
+   \begin{center}
+     \includegraphics[width=4.25in]{figures/lumobars.pdf}
+   \end{center}
+   % \caption{LUMO Results}
+   \label{fig:scan}
+ \end{figure}
+
+\section{Conclusions}
+
+Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors.
+The optimized parameters for the method were $C \approx 10$ and $\gamma \approx 0.05$.
+
+For the feature vectors, the decay was the best performing feature vector with the parameters $A = 1, H = 1, p = 1$.
+(0.71) As well as having a better overall performance, it is also much faster than the naive feature vector because it has fewer components.
+This increased speed could especially be seen when training the data.
+With the addition of predicted HOMO/LUMO values for the decay feature vector, the performance for estimating the goal features increased by about 25\%.
+
+Unexpectedly, the decay function with distance corrections did not perform any better than the regular decay feature vector.
+In theory, this should have worked better with heterogeneous side chains, but its use seemed to only increase the MAE.
+
+There were a few anomalies in the results.
+The most noticeable is the long tail distribution of errors.
+A few molecules within the set had unusually high band gap errors (ex: $8A\_TON\_A\_A$, 1.1 eV).
+structures where features overlap ($A\_TON\_4ed\_A$, 0.5 eV)
+
+To run the original DFT and TDDFT calculations for these molecules took about 35,0000 CPU hours. Calculating the same properties using these machine learning methods took about 4 seconds.
+
+\section{Future Work}
+
+For possible future work, the first thing to do would be to collect more data.
+For this study, the majority of the structures were monomers with 1-4 rings out from the core.
+This could be expanded to include larger polymers and monomers.
+
+None of the feature vectors take into account the Kuhn expression for polymer chains.
+This leads to high errors as n or m > 1.
+The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay (?).
+Preliminary work with this addition corrected seems to be the best way to account for polymerization of benzobisazoles.
+
+Another possible expansion of work would be to test with more properties of the molecules such as total energy, dipole, and etc.
+
+As an end goal, it would be nice to generalize these machine learning methods such that they could be used for any structure.
+
+% In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions.
+Unfortunatly, the results were not satisfactory relative to the amount of time required (0.20 eV MAE).
+Drastic changes to the network made minimal differences to the final error.
+This is attirbuted to inexperience with proper methodologies with Neural Networks.
+
+\nocite{ruddigkeit_enumeration_2012}
+\nocite{darley_beyond_2008}
+\nocite{frisch_gaussian_2009}
+\nocite{montavon_machine_2013}
+\nocite{handley_dynamically_2009}
+\nocite{hansen_assessment_2013}
+\nocite{schutt_how_2013}
+\nocite{reymond_exploring_2012}
+\nocite{whitfield_computational_2013}
+\nocite{hansen_assessment_2013-1}
+\nocite{ra_dft_2008}
+\nocite{martell_assessment_1997}
+\nocite{montavon_learning_2012}
+\nocite{domingos_few_2012}
+\nocite{martin_benchmark_1997}
+\nocite{handley_potential_2010}
+\nocite{rupp_fast_2012}
+
+\bibliography{paper}
+\newpage
+\appendix
 
@@
 \end{table}
-
- \begin{figure}[H]
-   \begin{center}
-     \includegraphics[width=5in]{figures/gapbars.pdf}
-   \end{center}
-   \caption{Band Gap Results}
-   \label{fig:scan}
- \end{figure}
 
@@
 
- \begin{figure}[H]
-   \begin{center}
-     \includegraphics[width=5in]{figures/homobars.pdf}
-   \end{center}
-   \caption{HOMO Results}
-   \label{fig:scan}
- \end{figure}
-
 % dummy            0.4330672042 $\pm$ 0.0380947474
@@
 
- \begin{figure}[H]
-   \begin{center}
-     \includegraphics[width=5in]{figures/lumobars.pdf}
-   \end{center}
-   \caption{LUMO Results}
-   \label{fig:scan}
- \end{figure}
-
 % dummy           0.4475990362 $\pm$ 0.0379190939
@@
 
-\section{Conclusions}
-
-Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors.
-The optimized paramters for the method were $C \approx 10$ and $\gamma \approx 0.05$.
-
-For the feature vectors, the decay was the best performaing feature vector with the parameters $A = 1, H = 1, p = 1$.
-(0.71) As well as having a better overall performance, it is also much faster than the naive feature vector because it has fewer components.
-This increased speed could especially be seen when training the data.
-With the addition of predicted HOMO/LUMO values for the decay feature vector, the performance for estimating the goal features increased by about 25\%.
-
-Unexpectedly, the decay function with distance corrections did not perform any better than the regular decay feature vector.
-In theory, this should have worked better with hetrogenous side chains, but its use seemed to only increase the MAE.
-
-There were a few anomalies in the results. The most noticeable is long tail distribution of errors ...
-several molecules with unusually high errors ($8A\_TON\_A\_A$), structures where features overlap ($A\_TON\_4ed\_A$)
-
-To run the original DFT and TDDFT calculations for these moelcules took about 35,0000 CPU hours. Calculating the same properties using these machine learning methods took about 4 seconds.
-
-% In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions.
-Unfortunatly, the results were not satisfactory relative to the amount of time required (0.20 eV MAE).
-Drastic changes to the network made minimal differences to the final error.
-This is attirbuted to inexperience with proper methodologies with Neural Networks.
-
-\section{Future Work}
-
-Continue making tweaks to reduce error
-Collect more data
-
-None of the feature vectors take into account the kuhn expression for polymer chains.
-This leads to high errors as n or m > 1.
-The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay (?).
-Preliminary work with this addition corrected seems to be the best way to account for polymerization of benzobisazoles.
-Test with additional properties (total energy, dipole, etc.)
-Generalize for any structure
-Make it faster
-% In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions.
-Unfortunatly, the results were not satisfactory relative to the amount of time required (0.20 eV MAE).
-Drastic changes to the network made minimal differences to the final error.
-This is attirbuted to inexperience with proper methodologies with Neural Networks.
-
-\nocite{ruddigkeit_enumeration_2012}
-\nocite{darley_beyond_2008}
-\nocite{frisch_gaussian_2009}
-\nocite{montavon_machine_2013}
-\nocite{handley_dynamically_2009}
-\nocite{hansen_assessment_2013}
-\nocite{schutt_how_2013}
-\nocite{reymond_exploring_2012}
-\nocite{whitfield_computational_2013}
-\nocite{hansen_assessment_2013-1}
-\nocite{ra_dft_2008}
-\nocite{martell_assessment_1997}
-\nocite{montavon_learning_2012}
-\nocite{domingos_few_2012}
-\nocite{martin_benchmark_1997}
-\nocite{handley_potential_2010}
-\nocite{rupp_fast_2012}
-
-\bibliography{paper}
-\newpage
-\appendix
-
 \end{document}

### 2014-06-20 paper/paper.tex
Update the paper

@@
 \title{Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles}
-\author{Christopher Collins}
+\author{Christopher Collins \and Aim\'{e}e Tomlinson}
 
@@
 \begin{abstract}
-By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively.
-These results also come with the added benefit of being 30,000,000 times faster than the equivalent Density Functional Theory calculation.
+Because there is always more molecules than time, there is a need to quickly be able to rule out structures that are unsuitable for further research.
+The method presented here takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations.
+By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for benzobisazoles.
+These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculation.
 \end{abstract}
 
-\doublespace
+% \doublespace
 \section{Introduction}
 
-There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor effeciency [CITE]. Computational
+There are many different molecule groups that are being looked at for use as organic solar cells [CITE]. One such group is the benzobisazoles [CITE].
+
+There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor efficiency [CITE].
+To attempt to search through all the possible compounds that could be used for organic solar cells computational methods are used to save time.
 
@@
 This naming scheme exploits the planar nature of benzobisazoles as well as their cruxiformic structure.
+Because of this regularity, they can be readily be structured in such a way that
 The naming scheme is broken down into three separate components. These parts are the core, the sides, and the options.
@@
   \caption{Aryl Groups}
+  \label{fig:aryl}
 \end{figure}
 
-\begin{table}[H]
-  \centering
-  \caption{Aryl Groups}
-  \begin{tabular}{lc}
-    Label   & Name                    \\
-    \hline
-    2       & Double Bond             \\
-    3       & Triple Bond             \\
-    4       & Phenyl                  \\
-    5       & Thiophene               \\
-    6       & Pyridine                \\
-    7       & Carbazole               \\
-    8       & Tetrazine               \\
-    9       & Ethylenedioxythiophene  \\
-    \hline
-  \end{tabular}
-  \label{tab:aryl}
-\end{table}
+These aryl groups are specifically were chosen because they are all highly conjugated. (NEEDS MORE)
 
 Each side is then broken down into components of Aryl, X groups, and R groups.
-Aryl groups are indicated by the numbers 2 through 9 as seen in Table \ref{tab:aryl}.
+Aryl groups are indicated by the numbers 2 through 9 as seen in Figure \ref{fig:aryl}.
 Aryl groups form the main chain part of the structure, they are able to extend the length of the chain and some have places for R groups (4, 5, 6, 7).
@@
 
+The X and R groups were picked based on their electron withdrawing/donating characteristics.
+These functional groups have also been shown to aide in the tuning of the optoelectronic properties of molecules [CITE].
+
 X and R groups are both composed of the same set of substituents seen in Table \ref{tab:xrgroups}.
-X groups are the letters A through L, and r groups are a through l.
+X groups are the letters $A$ through $L$, and R groups are $a$ through $l$.
 The main difference between X and R groups is where they are placed in the chain, whereas R-Groups are placed on the Aryl group that directly proceeds them.
@@
 As an end goal, it would be nice to generalize these machine learning methods such that they could be used for any structure.
+
+...
+The methods presented here would be used as a first line filter to rule out large amounts molecular structures that do not meet the desired requirements such that more time could be allocated only on the structures that show the most promise instead of relying on intuition.
+As can be seen by these methods speeds and relative accuracy, they fit the bill for this kind of work.
 

### 2014-06-20 paper/paper.tex
Add more to the paper

@@
 \title{Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles}
-\author{Christopher Collins \and Aim\'{e}e Tomlinson}
+\author{Christopher Collins \qquad Aim\'{e}e Tomlinson\\
+        \emph{Department of Chemistry and Biochemistry}\\
+         \emph{University of North Georgia}\\
+         \emph{Dahlonega, GA 30597}}
 
@@
 
-There are many different molecule groups that are being looked at for use as organic solar cells [CITE]. One such group is the benzobisazoles [CITE].
-
+There are many different molecule groups that are being looked at for use as organic solar cells [CITE].
+One such group is the benzobisazoles [CITE].
 There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor efficiency [CITE].
 To attempt to search through all the possible compounds that could be used for organic solar cells computational methods are used to save time.
+
+Density functional theory calculations have been used extensively to be able to predict the properties at a nice medium between the accuracy of \emph{ab inito} and the speed of semi empirical methods.
+Unfortunately, while they are faster than \emph{ab inito} calculations, DFT calculations still take a lot longer than to be desired.
+This problem is compounded when much of the interest in computational chemistry is being able to test molecules more quickly than could be done in the lab.
 
@@
 For this study, we will be looking at using different machine learning methods in conjunction with Density Functional Theory calculations to be able to predict the highest occupied molecular orbital (HOMO), lowest unoccupied molecular orbital (LUMO), and the band gap.
+The end goal of such methods being that they are faster ways to predict properties, but yet still retain enough accuracy such that they can be used to make quantitative ....
+about which structures would be of the most interest.
+
+There are many common features that are seen in many molecules, things like methyls, phenyls, and thiophenes so the goal of this is to make use of the fact that those structures have already been computed many times before, and one might expect that on average there is a common effect of each given group that can be used such that it does not require recomputing all of those effects for ever single instance of the feature.
+(By using that similarity, we expect to make calculations faster.)
 
@@
 This naming scheme exploits the planar nature of benzobisazoles as well as their cruxiformic structure.
-Because of this regularity, they can be readily be structured in such a way that
-The naming scheme is broken down into three separate components. These parts are the core, the sides, and the options.
+Because of this regularity, they can be readily be structured in such a way that they can be converted into a format that is easy to represent to the machine learning algorithms.
+The naming scheme is broken down into three separate components.
+These parts are the core, the sides, and the options.
 
@@
 
-These aryl groups are specifically were chosen because they are all highly conjugated. (NEEDS MORE)
+These aryl groups are specifically were chosen because they are all highly conjugated.
+These structures in particular have also been shown to be useful in the tuning of optoelectronic properties of benzobisazoles [CITE].
+(NEEDS MORE)
 
@@
 The X and R groups were picked based on their electron withdrawing/donating characteristics.
-These functional groups have also been shown to aide in the tuning of the optoelectronic properties of molecules [CITE].
+Just like with the aryl groups, these functional groups have also been shown to aid in the tuning of the optoelectronic properties of molecules [CITE].
+Previous work with these structures has also shown that HOMO and LUMO values have a strong correlation with the Hammet parameters of each of these functional groups (include?).
 
@@
 The main difference between X and R groups is where they are placed in the chain, whereas R-Groups are placed on the Aryl group that directly proceeds them.
-As can be seen in Table \ref{tab:aryl} R-groups come in pairs of two.
+As can be seen in Figure \ref{fig:aryl} R-groups come in pairs of two.
 These groups can either be the same or different(?).
@@
 
-Structures were picked using this naming scheme to try to cover as many combinations of cores, sides, and options.
-
 \section{Feature Vectors}
@@
 From the regular structure of the benzobisazoles, this can be done at the aryl group triplet level.
+For each aryl group triplet as they extend out from the core, a boolean vector based on the components of the triplet is formed.
 The problem with this approach is that is the size of the feature vector groups proportional to the length of the longest side chain.
+This can be especially problematic if some of the training molecules are much larger than the others.
 Another problem with this type of feature vector it does not exploit similarities in the structure.
@@
 To counter act these problems a second feature vector was created that used a decay function \eqref{decay}.
-$A$, $H$, and $p$ are arbitrary constants used to adjust the decay.
+$A$, $H$, and $p$ are arbitrary constants used to adjust the rate of decay.
 By grouping similar components together, it normalizes implicit features (charge, Hammet parameters, and etc).
@@
 In previous work \cite{montavon_machine_2013}, it has been shown that different machine learning algorithms have had drastically different performance when used to predict molecular properties.
-Because of this, seven algorithms were picked to compare.
+Because of this, seven algorithms were picked for comparison.
 These were mean value, linear regression, linear ridged regression, tree regression, k-nearest neighbors, and support vector machines.
-The mean value method is used as a baseline for all of the other methods.
+The support vector machines method was then broken down into two methods, one using a gaussian kernel, and the other using a laplacian kernel.
+All of the algorithms used were (000000000) from scikit-learn [CITE].
+The mean value method is used as a baseline for all of the other methods with its interpretation being the error that would be gotten by just guessing.
 
@@
    \end{center}
-   \caption{Scan of SVM parameters C and $\gamma$}
+   \caption{Example scan of test errors (eV) as a function of SVM parameters C and $\gamma$.
+The minimum located in the center corresponding to the ideal pair of parameter values to use for the machine learning model.}
    \label{fig:scan}
@@
 
-Roughly 1100 benzobisazole structures were built.
-Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*.
+Roughly 1100 benzobisazole structures were picked to to cover as many combinations of cores, sides, and options as possible.
+In terms of aryl triplets, all of the structures comprised of at most 4 triplets per side.
+(This allowed for a constant vector size for the naive feature vector.) (Many of these structures were from prior studies of different features of benzobisazoles) Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*.
 After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*.
 Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.
+The DFT calculations were done on using the computing cluster Marcy from Bucknell.
 
@@
 
-Once all the data and feature vectors were collected, they were feed into the machine learning algorthms.
+Once all the data and feature vectors were collected, they were feed into the machine learning algorithms.
 For each feature vector, property, method set the methods relevant parameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors).
-Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds.
+Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds [CITE].
 All of the results were then tabulated and compared based on their mean absolute errors (MAE) calculated as the distance the ML predicted value was from DFT calculated value.
+All of the machine learning calculations were done on a consumer single quad core computer.
 
@@
    \begin{center}
-     \includegraphics[width=4.25in]{figures/gapbars.pdf}
+     \includegraphics[width=5.5in]{figures/allbars2.pdf}
    \end{center}
-   % \caption{Band Gap Results}
-   \label{fig:scan}
- \end{figure}
-
- \begin{figure}[H]
-   \begin{center}
-     \includegraphics[width=4.25in]{figures/homobars.pdf}
-   \end{center}
-   % \caption{HOMO Results}
-   \label{fig:scan}
- \end{figure}
-
- \begin{figure}[H]
-   \begin{center}
-     \includegraphics[width=4.25in]{figures/lumobars.pdf}
-   \end{center}
-   % \caption{LUMO Results}
-   \label{fig:scan}
+   \caption{Results}
+   \label{fig:results}
  \end{figure}
@@
 Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors.
-The optimized parameters for the method were $C \approx 10$ and $\gamma \approx 0.05$.
+This matches similarly too the results seen by ....
+[CITE]; however, they found that the laplacian kernel performed the best.
+The suspected reason for the difference in the two results is thought to be because their method involved single atoms as features, whereas this method was dealing with entire functional groups.
+The smoothness of the gaussian distribution is probably a better estimator in that (especially with something like a phenyl ring).
+The optimized parameters for the method were found to be $C \approx 10$ and $\gamma \approx 0.05$.
 
@@
 None of the feature vectors take into account the Kuhn expression for polymer chains.
-This leads to high errors as n or m > 1.
+This leads to high errors when $n>1$ or $m>1$.
 The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay (?).
@@
 
-...
 The methods presented here would be used as a first line filter to rule out large amounts molecular structures that do not meet the desired requirements such that more time could be allocated only on the structures that show the most promise instead of relying on intuition.
-As can be seen by these methods speeds and relative accuracy, they fit the bill for this kind of work.
+As can be seen by these methods speeds and relative accuracy, these machine learning methods work really well for this task.
+In the same amount of time that one could calculate a property of a structure using DFT the same property can be predicted here for millions of structures.
+From those structures one could imagine taking the best 1\% of the structures and running progressively more accurate methods.
 
 % In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions.
-Unfortunatly, the results were not satisfactory relative to the amount of time required (0.20 eV MAE).
+Unfortunately, the results were not satisfactory relative to the amount of time required (0.20 eV MAE).
 Drastic changes to the network made minimal differences to the final error.
-This is attirbuted to inexperience with proper methodologies with Neural Networks.
+This is attributed to inexperience with proper methodologies with Neural Networks.
+% Also, the methods mentioned in \cite{hansen_assessment_2013} were tested and the results were not as good as any of the other name based features (0.25-0.35 eV).
+In addition to the accuracy problems, it had severe performance problems because it relys on $O(n^2)$ elements in each feature vector where $n$ is the number of atoms in the structure.
 

### 2014-06-22 paper/paper.tex
Add highlighting to paper for comment sections

@@
 \usepackage{url}
+\usepackage{color}
+\usepackage{soul}
 \usepackage{setspace}
@@
 \begin{abstract}
-Because there is always more molecules than time, there is a need to quickly be able to rule out structures that are unsuitable for further research.
+Because there are always more molecules to test than time, there is a need to quickly be able to rule out structures that are unsuitable for further research.
 The method presented here takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations.
@@
 
-There are many different molecule groups that are being looked at for use as organic solar cells [CITE].
-One such group is the benzobisazoles [CITE].
-There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor efficiency [CITE].
+There are many different molecule groups that are being looked at for use as organic solar cells \hl{[CITE]}.
+One such group is the benzobisazoles \hl{[CITE]}.
+There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor efficiency \hl{[CITE]}.
 To attempt to search through all the possible compounds that could be used for organic solar cells computational methods are used to save time.
@@
 For this study, we will be looking at using different machine learning methods in conjunction with Density Functional Theory calculations to be able to predict the highest occupied molecular orbital (HOMO), lowest unoccupied molecular orbital (LUMO), and the band gap.
-The end goal of such methods being that they are faster ways to predict properties, but yet still retain enough accuracy such that they can be used to make quantitative ....
-about which structures would be of the most interest.
+The end goal of such methods being that they are faster ways to predict properties, but yet still retain enough accuracy such that they can be used to make quantitative \hl{....} about which structures would be of the most interest.
 
@@
   \caption{Aryl Groups}
-  \label{fig:aryl}
+  \label{fig:Aryl}
 \end{figure}
 
-These aryl groups are specifically were chosen because they are all highly conjugated.
-These structures in particular have also been shown to be useful in the tuning of optoelectronic properties of benzobisazoles [CITE].
-(NEEDS MORE)
+These Aryl groups are specifically were chosen because they are all highly conjugated.
+These structures in particular have also been shown to be useful in the tuning of optoelectronic properties of benzobisazoles \hl{[CITE].
+(NEEDS MORE)}
 
 Each side is then broken down into components of Aryl, X groups, and R groups.
-Aryl groups are indicated by the numbers 2 through 9 as seen in Figure \ref{fig:aryl}.
+Aryl groups are indicated by the numbers 2 through 9 as seen in Figure \ref{fig:Aryl}.
 Aryl groups form the main chain part of the structure, they are able to extend the length of the chain and some have places for R groups (4, 5, 6, 7).
@@
 The X and R groups were picked based on their electron withdrawing/donating characteristics.
-Just like with the aryl groups, these functional groups have also been shown to aid in the tuning of the optoelectronic properties of molecules [CITE].
-Previous work with these structures has also shown that HOMO and LUMO values have a strong correlation with the Hammet parameters of each of these functional groups (include?).
+Just like with the Aryl groups, these functional groups have also been shown to aid in the tuning of the optoelectronic properties of molecules \hl{[CITE]}.
+Previous work with these structures has also shown that HOMO and LUMO values have a strong correlation with the Hammet parameters of each of these functional groups \hl{(include?)}.
 
@@
 The main difference between X and R groups is where they are placed in the chain, whereas R-Groups are placed on the Aryl group that directly proceeds them.
-As can be seen in Figure \ref{fig:aryl} R-groups come in pairs of two.
-These groups can either be the same or different(?).
+As can be seen in Figure \ref{fig:Aryl} R-groups come in pairs of two.
+These groups can either be the same or different\hl{(?)}.
 Because there are some Aryl groups that do not allow any R-groups there is an additional spacer R-group that is designated as *.
@@
 They are either an X-group (which terminates the entire side) or they are a triplet of an Aryl group and two R-groups.
-If it is an aryl group triplet, then the process can continue.
+If it is an Aryl group triplet, then the process can continue.
 (X-group $\vert$ [Aryl, R-group, R-group])
@@
 These are broken up into two main classes.
-The first pair of options are the polymer options and they indicate how many times the molecules is repeated along the horizontal (n) axis (chain?) or the vertical (m) axis (chain?).
-The second set of options is a set of x, y, and z that are the number of times that the molecule is stacked in each direction(?).
+The first pair of options are the polymer options and they indicate how many times the molecules is repeated along the horizontal (n) axis \hl{(chain?)} or the vertical (m) axis \hl{(chain?)}.
+The second set of options is a set of x, y, and z that are the number of times that the molecule is stacked in each direction\hl{(?)}.
 
@@
 
-The first, and most simplistic, is to take all the possible combinations and create a binary vector from it with each 1 in a location representing a particular combination.
-From the regular structure of the benzobisazoles, this can be done at the aryl group triplet level.
-For each aryl group triplet as they extend out from the core, a boolean vector based on the components of the triplet is formed.
+The first, and most simplistic, is to take all the possible combinations and create a binary vector from it with each $1$ in a location representing a particular combination.
+From the regular structure of the benzobisazoles, this can be done at the Aryl group triplet level.
+For each Aryl group triplet as they extend out from the core, a boolean vector based on the components of the triplet is formed.
 The problem with this approach is that is the size of the feature vector groups proportional to the length of the longest side chain.
@@
 The support vector machines method was then broken down into two methods, one using a gaussian kernel, and the other using a laplacian kernel.
-All of the algorithms used were (000000000) from scikit-learn [CITE].
+All of the algorithms used were \hl{(000000000) from scikit-learn [CITE]}.
 The mean value method is used as a baseline for all of the other methods with its interpretation being the error that would be gotten by just guessing.
@@
 Roughly 1100 benzobisazole structures were picked to to cover as many combinations of cores, sides, and options as possible.
-In terms of aryl triplets, all of the structures comprised of at most 4 triplets per side.
+In terms of Aryl triplets, all of the structures comprised of at most 4 triplets per side.
 (This allowed for a constant vector size for the naive feature vector.) (Many of these structures were from prior studies of different features of benzobisazoles) Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*.
@@
 Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.
-The DFT calculations were done on using the computing cluster Marcy from Bucknell.
+The DFT calculations were done using the computing cluster Marcy from Bucknell and Gaussian 09.
+The machine learning algorithms used were the ones implemented in the \hl{Scikit-Learn Python Library}.
 
@@
 All of the results were then tabulated and compared based on their mean absolute errors (MAE) calculated as the distance the ML predicted value was from DFT calculated value.
-All of the machine learning calculations were done on a consumer single quad core computer.
+All of the machine learning calculations were done on a single consumer quad core computer.
 
@@
 Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors.
-This matches similarly too the results seen by ....
-[CITE]; however, they found that the laplacian kernel performed the best.
+This matches similarly too the results seen by \hl{....
+[CITE]}; however, they found that the laplacian kernel performed the best.
 The suspected reason for the difference in the two results is thought to be because their method involved single atoms as features, whereas this method was dealing with entire functional groups.
@@
 For the feature vectors, the decay was the best performing feature vector with the parameters $A = 1, H = 1, p = 1$.
-(0.71) As well as having a better overall performance, it is also much faster than the naive feature vector because it has fewer components.
+\hl{(0.71)} As well as having a better overall performance, it is also much faster than the naive feature vector because it has fewer components.
 This increased speed could especially be seen when training the data.
@@
 This leads to high errors when $n>1$ or $m>1$.
-The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay (?).
+The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay \hl{(?)}.
 Preliminary work with this addition corrected seems to be the best way to account for polymerization of benzobisazoles.
@@
 
+\hl{preliminary results have shown that the naive feature vector works the best with predicting total energy (117 hartree MAE with svm, 2800 hartree MAE with mean) (about 2x as effective).
+This could be because the total energy is more dependent on the structure as a whole rather than the localization to the core.}
+
 As an end goal, it would be nice to generalize these machine learning methods such that they could be used for any structure.
+While the but perhaps there is a way to do it based off localized functional groups.
 
@@
 
-% In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions.
+\hl{In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions.
 Unfortunately, the results were not satisfactory relative to the amount of time required (0.20 eV MAE).
 Drastic changes to the network made minimal differences to the final error.
-This is attributed to inexperience with proper methodologies with Neural Networks.
-% Also, the methods mentioned in \cite{hansen_assessment_2013} were tested and the results were not as good as any of the other name based features (0.25-0.35 eV).
+This is attributed to inexperience with proper methodologies with Neural Networks.}
+\hl{Also, the methods mentioned in }\cite{hansen_assessment_2013} \hl{were tested and the results were not as good as any of the other name based features (0.25-0.35 eV).
 In addition to the accuracy problems, it had severe performance problems because it relys on $O(n^2)$ elements in each feature vector where $n$ is the number of atoms in the structure.
+To save time, only structures with <45 atoms total were tested, leaving about 450 structures.}
 

### 2014-06-27 paper/paper.tex
Add updates to the paper

@@
 The method presented here takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations.
-By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for benzobisazoles.
+By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for the benzobisazole structures tested.
 These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculation.
@@
 
-\section{Naming Scheme}
+\section{Systems of Interest}
+
+For this study, we will be looking at the optoelectronic properties of benzobisazoles, a class of molecules comprised of a three fused ring core.
+This core is crucial in the fact that it it is highly conjugated which allows for better electron transfer and consequently make them better as organic solar cells.
+In addition to the core of the benzobisazole there are four different directions from the core that can be extended with various rings and other conjugated systems to attempt to tune the properties of the molecule.
+
+To aid in electron transfer, these structures were picked such that they were highly planer \hl{(angle function?)}
+
+\subsection{Naming Scheme}
 
@@
 
+\begin{figure}[H]
+  \begin{center}
+    \includegraphics[width=4.5in]{figures/features.pdf}
+  \end{center}
+  \caption{Visual Representations of the respective Feature Vector types. \textbf{1.} Naive. \textbf{2.} Decay. \textbf{3.} Decay with length corrections.}
+  \label{fig:features}
+\end{figure}
+
 \subsection{Decay with Predictions}
@@
 The mean value method is used as a baseline for all of the other methods with its interpretation being the error that would be gotten by just guessing.
+
+\hl{????}
+\subsection{Mean Value}
+\subsection{Linear Regression}
+\subsection{Linear Ridge Regression}
+\subsection{Tree Regression}
+\subsection{k-Nearest Neighbors}
+\subsection{Support Vector Machines}
+\subsubsection{Gaussian Kernel}
+\subsubsection{Laplacian Kernel}
+\hl{????}
 
@@
    \end{center}
-   \caption{Results}
+   \caption{Results.
+The far left column of each of the graphs can be seen as a baseline value for the set.
+So from there, any values that are lower than that value are better (with the optimal value being 0.0 eV).
+For the numerical values, refer to the Appendix.}
    \label{fig:results}
@@
 Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors.
-This matches similarly too the results seen by \hl{....
+This matches similarly to the results seen by \hl{....
 [CITE]}; however, they found that the laplacian kernel performed the best.
@@
   \end{tabular}
-  \label{tab:gapresults}
+  \label{tab:lumoresults}
 \end{table}

### 2014-06-30 paper/paper.tex
Add updates to the paper

@@
 
-To aid in electron transfer, these structures were picked such that they were highly planer \hl{(angle function?)}
+For the side chains, structures were picked based on their ability to tune electronic properties.
+In the case of the main backbone structures, they were all picked because they are all highly planar and highly conjugated.
+Both of these features to aid in electron transfer.
+For the various substiuents, they picked based off their known ability to tune electronic properties \hl{(repeating...)}.
+The properties of this study have been shown in previous research to be correlated with Hammett Parameters.
+\hl{cool story...}
 
@@
 
-To be able to represent these molecular structures to the machine learning algorithms, a common naming scheme was formed such that it could be readily converted into a vector form.
+Unfortunately, the machine learning algorithms used for this study do not natively understand molecular structures and instead only are able to function on vector forms.
+To rectify this, a common naming scheme was formed such that it could be readily converted into a vector form.
 This naming scheme exploits the planar nature of benzobisazoles as well as their cruxiformic structure.
@@
 
-The core is the central three fused ring system of the benzobisazoles.
+The core part of the structure is composed of a single three fused ring system.
 All cores are identified by a combination of three letters.
@@
 In theory, this should have worked better with heterogeneous side chains, but its use seemed to only increase the MAE.
+We think that the cause of this is due to the lack of sampling of largely heterogeneous side chains.
+So perhaps, if the same tests were done with only heterogeneous side chains adding the correction factor might decrease the total error.
 
@@
 The most noticeable is the long tail distribution of errors.
-A few molecules within the set had unusually high band gap errors (ex: $8A\_TON\_A\_A$, 1.1 eV).
-structures where features overlap ($A\_TON\_4ed\_A$, 0.5 eV)
+As one might expect, structures where features overlap ($A\_TON\_4ed\_A$, 0.5 eV) there were higher MAE values.
+Unfortunately, a few molecules within the set had unusually high band gap errors (ex: $8A\_TON\_A\_A$, 1.1 eV) and we have no explanation for why that occurred.
 
-To run the original DFT and TDDFT calculations for these molecules took about 35,0000 CPU hours. Calculating the same properties using these machine learning methods took about 4 seconds.
+To run the original DFT and TDDFT calculations for these molecules took about 35,0000 CPU hours.
+Calculating the same properties using these machine learning methods took about 4 seconds for each property for all 1100 structures.
+Because of the way that machine learning algorithms work, the majority of the time spent for each of these calculations is spent in the training phase; fortunately, this calculation is only required once so by .
+Once the models have been trained, these calculations are often reduced to just matrix multiplications leading to it taking just 0.1 seconds to calculate each property for all 1100 structures.
 
@@
 For this study, the majority of the structures were monomers with 1-4 rings out from the core.
-This could be expanded to include larger polymers and monomers.
+This could be expanded to include larger polymers and monomers, especially with an emphasis on having more heterogeneous side chains.
+The functional groups could also be expanded to include things such as furan, pyrrole, or other conjugated systems.
 
 None of the feature vectors take into account the Kuhn expression for polymer chains.
+Because many of these machine learning algorithms use linear models to fit, they do not accurately represent the nonlinear decay of influence seen in long polymers.
 This leads to high errors when $n>1$ or $m>1$.
 The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay \hl{(?)}.
-Preliminary work with this addition corrected seems to be the best way to account for polymerization of benzobisazoles.
+\hl{Some preliminary work was done with predicting n=1,2,3,4 and then fitting the Kuhn expression for long polymers.
+This additional correction seems to be a good way to account for polymerization of benzobisazoles.}
+
+% \begin{table}[H]
+%   \centering
+%   \caption{TON\_n20}
+%   \begin{tabular}{lrrr}
+%             Type      & HOMO (eV) & LUMO (eV) & Band Gap (eV) \\
+%     \hline\hline
+%             Predicted & -5.59 & -2.36 & 2.73 \\
+%             Corrected & -5.99 & -3.36 & 2.13 \\
+%             Actual    & -5.96 & -3.48 & 2.17 \\
+%     \hline\hline
+%   \end{tabular}
+%   \label{tab:TONn20}
+% \end{table}
+
+% \begin{table}[H]
+%   \centering
+%   \caption{TON\_m20}
+%   \begin{tabular}{lrrr}
+%             Type      & HOMO (eV) & LUMO (eV) & Band Gap (eV) \\
+%     \hline\hline
+%             Predicted & -5.61 & -2.34 & 2.73 \\
+%             Corrected & -5.84 & -2.20 & 3.10 \\
+%             Actual    & -5.73 & -2.16 & 3.14 \\
+%     \hline\hline
+%   \end{tabular}
+%   \label{tab:TONm20}
+% \end{table}
 
 Another possible expansion of work would be to test with more properties of the molecules such as total energy, dipole, and etc.
-
 \hl{preliminary results have shown that the naive feature vector works the best with predicting total energy (117 hartree MAE with svm, 2800 hartree MAE with mean) (about 2x as effective).
@@
 As an end goal, it would be nice to generalize these machine learning methods such that they could be used for any structure.
-While the but perhaps there is a way to do it based off localized functional groups.
+\hl{While the} but perhaps there is a way to do it based off localized functional groups.
 
@@
 In addition to the accuracy problems, it had severe performance problems because it relys on $O(n^2)$ elements in each feature vector where $n$ is the number of atoms in the structure.
-To save time, only structures with <45 atoms total were tested, leaving about 450 structures.}
+To save time, only structures with $<45$ atoms total were tested, leaving about 450 structures.}
 

### 2014-07-01 paper/paper.tex
Add updates to the paper

@@
 Since the effects of atoms are highly dependent on distance this sort of assumption is problematic for heterogeneous side groups.
-\eqref{decay2} Something something.
+\eqref{decay2} \hl{Something something}.
 This normalizes all the lengths such that longer structures will increase the distance more than shorter structures.
@@
 
-\hl{????}
-\subsection{Mean Value}
-\subsection{Linear Regression}
-\subsection{Linear Ridge Regression}
-\subsection{Tree Regression}
-\subsection{k-Nearest Neighbors}
-\subsection{Support Vector Machines}
-\subsubsection{Gaussian Kernel}
-\subsubsection{Laplacian Kernel}
-\hl{????}
+\hl{???? information about the different methods used?}
+% \subsection{Mean Value}
+% \subsection{Linear Regression}
+% \subsection{Linear Ridge Regression}
+% \subsection{Tree Regression}
+% \subsection{k-Nearest Neighbors}
+% \subsection{Support Vector Machines}
+% \subsubsection{Gaussian Kernel}
+% $$k(x, x') = exp\left( - \frac{1}{2 \sigma^2} || x - x' ||^2 \right)$$
+% \subsubsection{Laplacian Kernel}
+% $$k(x, x') = exp\left( - \frac{1}{\sigma} | x - x' | \right)$$
 
@@
    \caption{Example scan of test errors (eV) as a function of SVM parameters C and $\gamma$.
-The minimum located in the center corresponding to the ideal pair of parameter values to use for the machine learning model.}
+The minimum located in the center corresponding to the ideal pair of parameter values to use for the machine learning model.
+Similar scan procedures were done for the parameters of the other models to find the lowest testing error.}
    \label{fig:scan}
@@
 After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*.
-Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.
-The DFT calculations were done using the computing cluster Marcy from Bucknell and Gaussian 09.
+\hl{Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.} The DFT calculations were done using the computing cluster Marcy from Bucknell and Gaussian 09.
 The machine learning algorithms used were the ones implemented in the \hl{Scikit-Learn Python Library}.

### 2014-07-02 paper/paper.tex
Add updates to the paper

@@
   \end{center}
-  \caption{TXY and CXY Cores}
+  \caption{TXY and CXY Cores. The $R^{H1}$, $R^v$, and $R^{H2}$ positions correspond to the left chain, the two vertical chains, and the right chain respectively.}
   \label{fig:cores}
@@
   \end{center}
-  \caption{Aryl Groups}
+  \caption{List of all the Aryl Groups and their respective identifiers. The $R^1$ and $R^2$ positions list possible places for added substituents.}
   \label{fig:Aryl}
@@
 Aryl groups are indicated by the numbers 2 through 9 as seen in Figure \ref{fig:Aryl}.
-Aryl groups form the main chain part of the structure, they are able to extend the length of the chain and some have places for R groups (4, 5, 6, 7).
+Aryl groups form the main chain part of the structure, they are able to extend the length of the chain and some have places for R groups (4, 5, 6, 7) to allow for better tuning of the optoelectronic properties.
 
@@
     C/c     & Bromine   \\
-    D/d     & CN        \\
-    E/e     & CCH       \\
-    F/f     & OH        \\
-    G/g     & SH        \\
-    H/h     & $NH_2$    \\
-    I/i     & $CH_3$    \\
+    D/d     & Cyano     \\
+    E/e     & Alkyne    \\
+    F/f     & Hydroxy   \\
+    G/g     & Thiol     \\
+    H/h     & Amine     \\
+    I/i     & Methyl    \\
     J/j     & Phenyl    \\
     K/k     & TMS       \\
-    L/l     & $OCH_3$   \\
+    L/l     & Methoxy   \\
     *       & Spacer    \\
@@
 X groups are the letters $A$ through $L$, and R groups are $a$ through $l$.
-The main difference between X and R groups is where they are placed in the chain, whereas R-Groups are placed on the Aryl group that directly proceeds them.
+The only difference between X and R groups is where they are placed in the chain.
+R-Groups are placed on in the $R^1$ and $R^2$ positions of Aryl groups, whereas X groups on the other hand attach to the ends of chains and terminate them.
 As can be seen in Figure \ref{fig:Aryl} R-groups come in pairs of two.
@@
 To be able to represent these structures to the computer, and consequently to the machine learning algorithms they must be vectorized.
+Fortunately, having a regular naming scheme as described is very beneficial in being able to vectorize these structures without having to account for every atom in the structure.
 
-Using this naming scheme, it is apparent that there are multiple ways that these could be converted into feature vectors for use in machine learning.
+Using this naming scheme, there are multiple ways that these names could be converted into feature vectors for use in machine learning. \hl{more}
 
@@
 \begin{equation}\label{decay}
-    Value = \sum_i^n (A d_i^{-H})^{p}
+    V = \sum_i^n (A d_i^{-H})^{p}
 \end{equation}
@@
 \begin{equation}\label{decay2}
-    Value = \sum_i^n \left(A \left(\frac{d_i}{M_i}\right)^{-H} \right)^{p}
+    V = \sum_i^n \left(A \left(\frac{d_i}{M_i}\right)^{-H} \right)^{p}
 \end{equation}
@@
 For each feature vector, property, method set the methods relevant parameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors).
-Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds [CITE].
+Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds \hl{[CITE]}.
 All of the results were then tabulated and compared based on their mean absolute errors (MAE) calculated as the distance the ML predicted value was from DFT calculated value.

### 2014-07-10 paper/paper.tex
Add update to paper

@@
 \begin{abstract}
-Because there are always more molecules to test than time, there is a need to quickly be able to rule out structures that are unsuitable for further research.
+\hl{Because there are always more molecules to test than time}, there is a need to quickly be able to rule out structures that are unsuitable for further research.
 The method presented here takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations.

### 2014-07-24 paper/paper.tex
Add some more to the paper

@@
 \hl{Because there are always more molecules to test than time}, there is a need to quickly be able to rule out structures that are unsuitable for further research.
-The method presented here takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations.
+The method presented in this paper takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations.
 By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for the benzobisazole structures tested.
@@
 Unfortunately, while they are faster than \emph{ab inito} calculations, DFT calculations still take a lot longer than to be desired.
-This problem is compounded when much of the interest in computational chemistry is being able to test molecules more quickly than could be done in the lab.
+This problem is compounded when one of the of the interests in computational chemistry is being able to test molecules more quickly than could be done in the lab.
 

### 2014-07-29 paper/paper.tex
Add some more updates to the paper

@@
 By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for the benzobisazole structures tested.
-These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculation.
+These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculations.
 \end{abstract}
@@
 One such group is the benzobisazoles \hl{[CITE]}.
-There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor efficiency \hl{[CITE]}.
-To attempt to search through all the possible compounds that could be used for organic solar cells computational methods are used to save time.
+To optimize the optoelectronic properties of molecules for use in solar cells, often various electron donating and electron accepting groups are added to the structure to shift electron density.
+For testing all of the possible structures (even in small sets) this is not feasible in the lab.
+To reduce some of the time required, and to expand the total search space, computational methods such as density functional theory have been used to predict the properties of molecules fairly rapidly.
+Unfortunately, these calculations also have their own limits in the amount of structures that can be tested in a reasonable time frame.
+ \hl{There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor efficiency [CITE].
+To attempt to search through all the possible compounds that could be used for organic solar cells computational methods are used to save time.}
 
@@
 The properties of this study have been shown in previous research to be correlated with Hammett Parameters.
-\hl{cool story...}
+\hl{cool story...} Some of the trends as seen in previous work are that adding electron donating groups to the vertical axis and electron withdrawing  groups to the horizontal axis lead to higher HOMO energies and lower LUMO which in turn leads to an overall lower band gap.
+Part of the goal of this study is to take these general trends and synthesize them into a model that imparts a useful numerical value.
 
@@
 $$ newLUMO = [Decay, predictedGAP, predictedHOMO] $$
+\hl{MAYBE ILLUSTRATIONS?}
 
@@
 The support vector machines method was then broken down into two methods, one using a gaussian kernel, and the other using a laplacian kernel.
-All of the algorithms used were \hl{(000000000) from scikit-learn [CITE]}.
 The mean value method is used as a baseline for all of the other methods with its interpretation being the error that would be gotten by just guessing.
+All of the algorithms utilized were as implemented in the \hl{scikit-learn python library [CITE]}.
 
@@
 In terms of Aryl triplets, all of the structures comprised of at most 4 triplets per side.
-(This allowed for a constant vector size for the naive feature vector.) (Many of these structures were from prior studies of different features of benzobisazoles) Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*.
+This allowed for a constant vector size for the naive feature vector.
+(Many of these structures were from prior studies of different features of benzobisazoles).
+Once they were built, the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*.
 After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*.
-\hl{Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.} The DFT calculations were done using the computing cluster Marcy from Bucknell and Gaussian 09.
+\hl{Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.} The DFT calculations were done using the computing cluster \hl{Marcy from Bucknell} and Gaussian 09.
 The machine learning algorithms used were the ones implemented in the \hl{Scikit-Learn Python Library}.
 
-Once all the calculations were completed, the resulting log files were parsed for HOMO, LUMO, and Band Gap values.
+Once all the DFT calculations were completed, the resulting log files were parsed for HOMO, LUMO, and Band Gap values.
 From there, the first three feature vectors were constructed (Naive, Decay, Decay with Distance Correction) and the resulting vectors were stored with the parsed log data.
@@
 As an end goal, it would be nice to generalize these machine learning methods such that they could be used for any structure.
-\hl{While the} but perhaps there is a way to do it based off localized functional groups.
+\hl{While the...} but perhaps there is a way to do it based off localized functional groups.
 

### 2014-08-14 paper/paper.tex
Update paper

@@
 One such group is the benzobisazoles \hl{[CITE]}.
-To optimize the optoelectronic properties of molecules for use in solar cells, often various electron donating and electron accepting groups are added to the structure to shift electron density.
+To optimize the optoelectronic properties of molecules for use in solar cells, various electron donating and electron accepting groups are added to the structure to shift electron density.
 For testing all of the possible structures (even in small sets) this is not feasible in the lab.
@@
 
-Because of these problems, there is a need to rapidly predict the properties of molecules so that.
-Machine learning has been shown to be a fast way to predict properties of many systems and specifically, has been shown to be a viable way to predict properties of molecules\cite{hansen_assessment_2013} \cite{montavon_machine_2013}.
+To take on both of both of these problems, we will be looking machine learning methods to both be able to predict molecular properties, but with the goal that these calculations would be inexpensive but retain the same level of accuracy.
+In recent work, various machine learning methods have been shown to be fast ways to predict properties of many systems and specifically, has been shown to be a viable way to predict properties of molecules\cite{hansen_assessment_2013} \cite{montavon_machine_2013}.
 
@@
 
-There are many common features that are seen in many molecules, things like methyls, phenyls, and thiophenes so the goal of this is to make use of the fact that those structures have already been computed many times before, and one might expect that on average there is a common effect of each given group that can be used such that it does not require recomputing all of those effects for ever single instance of the feature.
+There are many common functional groups and structural features that are seen repeated across many molecules, so the goal of this is to make use of the fact that those structures have already been computed many times before, and one might expect that on average there is a common effect of each given group that can be used such that it does not require recomputing all of those effects for ever single instance of the feature.
 (By using that similarity, we expect to make calculations faster.)
@@
 Just like with the Aryl groups, these functional groups have also been shown to aid in the tuning of the optoelectronic properties of molecules \hl{[CITE]}.
-Previous work with these structures has also shown that HOMO and LUMO values have a strong correlation with the Hammet parameters of each of these functional groups \hl{(include?)}.
+Previous work with these structures has also shown that HOMO and LUMO values have a strong correlation with the Hammet parameters of each of these functional groups \hl{(include?
+REPEAT...)}.
 
@@
 
-To be able to represent these structures to the computer, and consequently to the machine learning algorithms they must be vectorized.
-Fortunately, having a regular naming scheme as described is very beneficial in being able to vectorize these structures without having to account for every atom in the structure.
+Representations of molecular structures are \hl{asdsa}, unfortunately, this intuition of molecular structure is not understood by computers.
+Instead of holistic pictures of the entire structure, they are left with lists of atom coordinates and bond connections.
+\hl{This could possibly be done by images of molecular structures (MASSIVE amounts of data).}
 
-Using this naming scheme, there are multiple ways that these names could be converted into feature vectors for use in machine learning. \hl{more}
+To represent these structures to the computer, and consequently to the machine learning algorithms, they must be converted into some sort of a structured vector.
+Fortunately, starting from the naming scheme described simplifies a lot of this work in that it is very regular\hl{??}.
+It is also beneficial in that many of the components of the name are larger structural features instead of individual atoms which would require larger vectors \hl{(meaning more computation required)}.
+
+Using the naming scheme described, there are multiple ways that these names could be converted into feature vectors for use in machine learning.
+These range from methods purely from the different structural combinations to methods that take into account the cruxiformic structure of the benzobisazoles.
+\hl{more}
 
@@
 For each Aryl group triplet as they extend out from the core, a boolean vector based on the components of the triplet is formed.
+
 The problem with this approach is that is the size of the feature vector groups proportional to the length of the longest side chain.
@@
 Another problem with this type of feature vector it does not exploit similarities in the structure.
-(one might expect a chlorine two steps away from the core to cause about the same effect as one one step away times some decay factor).
+\hl{(one might expect a chlorine two steps away from the core to cause about the same effect as one one step away times some decay factor)}.
 
@@
 $A$, $H$, and $p$ are arbitrary constants used to adjust the rate of decay.
-By grouping similar components together, it normalizes implicit features (charge, Hammet parameters, and etc).
+This adjustment of feature structure allows the grouping similar components together which in turn gives an implicit normalization of specific component attributes (charge, Hammet parameters, electronegativity, and etc).
 
@@
 This would mean that there is no unique conversion between a given feature vector and its associated name/structure.
+\hl{In the case of using this method as a sieve, this is not an issue.}
 
@@
 
-$M_i$ is a normalizing factor for each segment in the chain. By doing this, all the lengths are normalized relative to the first element.
-
 \begin{equation}\label{decay2}
@@
 
+$M_i$ is a normalizing factor for each segment in the chain.
+By doing this, all the lengths are added to the chain are stored relative to the length of the first element in the chain.
 The problem with this feature vector is that it is not separable.
@@
 \subsection{Decay with Predictions}
+
+\hl{INSERT LINEAR LUMO-HOMO PLOT?}
 
@@
 $$ newLUMO = [Decay, predictedGAP, predictedHOMO] $$
-\hl{MAYBE ILLUSTRATIONS?}
+\hl{MAYBE ILLUSTRATIONS? instead of psuedocode...}
 
@@
 
-In previous work \cite{montavon_machine_2013}, it has been shown that different machine learning algorithms have had drastically different performance when used to predict molecular properties.
+In the work by Montavon et al., it has been shown that different machine learning algorithms have had drastically different performances when used to predict molecular properties.
 Because of this, seven algorithms were picked for comparison.
 These were mean value, linear regression, linear ridged regression, tree regression, k-nearest neighbors, and support vector machines.
-The support vector machines method was then broken down into two methods, one using a gaussian kernel, and the other using a laplacian kernel.
+The support vector machines method was then broken down into two methods, one using a Gaussian kernel, and the other using a Laplacian kernel.
 The mean value method is used as a baseline for all of the other methods with its interpretation being the error that would be gotten by just guessing.
-All of the algorithms utilized were as implemented in the \hl{scikit-learn python library [CITE]}.
 
@@
    \end{center}
-   \caption{Example scan of test errors (eV) as a function of SVM parameters C and $\gamma$.
-The minimum located in the center corresponding to the ideal pair of parameter values to use for the machine learning model.
-Similar scan procedures were done for the parameters of the other models to find the lowest testing error.}
+   \caption{Example scan of test errors (eV) as a function of SVM hyperparameters C and $\gamma$.
+The minimum located in the center corresponding to the ideal pair of hyperparameter values to use for the machine learning model.
+Similar scan procedures were done for the hyperparameters of the other models to find the lowest testing error.}
    \label{fig:scan}
@@
 Once they were built, the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*.
-After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*.
-\hl{Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.} The DFT calculations were done using the computing cluster \hl{Marcy from Bucknell} and Gaussian 09.
-The machine learning algorithms used were the ones implemented in the \hl{Scikit-Learn Python Library}.
+After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) again with B3LYP/6-31g*.
+\hl{Beyond the 1100 benzobisazole structures, about 1000 other structures were collected for comparison.}
 
-Once all the DFT calculations were completed, the resulting log files were parsed for HOMO, LUMO, and Band Gap values.
-From there, the first three feature vectors were constructed (Naive, Decay, Decay with Distance Correction) and the resulting vectors were stored with the parsed log data.
+Once all the DFT calculations were completed, the resulting log files were processed for the HOMO, LUMO, and Band Gap energy values.
+From there, the first three feature vectors were constructed (Naive, Decay, Decay with Distance Correction) and the resulting vectors were stored with the energy data.
 
 Once all the data and feature vectors were collected, they were feed into the machine learning algorithms.
-For each feature vector, property, method set the methods relevant parameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors).
-Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds \hl{[CITE]}.
+For each feature vector, property, method set the methods relevant hyperparameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors).
+Then using these optimized hyperparameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds \hl{[CITE]}.
 All of the results were then tabulated and compared based on their mean absolute errors (MAE) calculated as the distance the ML predicted value was from DFT calculated value.
-All of the machine learning calculations were done on a single consumer quad core computer.
 
@@
 
-Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors.
-This matches similarly to the results seen by \hl{....
-[CITE]}; however, they found that the laplacian kernel performed the best.
-The suspected reason for the difference in the two results is thought to be because their method involved single atoms as features, whereas this method was dealing with entire functional groups.
+Overall, the support vector machines with Gaussian kernel had the best performance across all of the machine learning methods and all of the feature vectors.
+This matches similarly to the results seen in \hl{....
+[CITE]}; however, they found that the Laplacian kernel performed the best.
+The suspected reason for the difference in the two results is thought to be because the method used in that study involved single atoms as features, whereas this method was dealing with entire functional groups.
 The smoothness of the gaussian distribution is probably a better estimator in that (especially with something like a phenyl ring).
-The optimized parameters for the method were found to be $C \approx 10$ and $\gamma \approx 0.05$.
+For the SVM with Gaussian kernel, the optimized hyperparameters to be $C \approx 10$ and $\gamma \approx 0.05$ for all of the properties.
 
@@
 This increased speed could especially be seen when training the data.
-With the addition of predicted HOMO/LUMO values for the decay feature vector, the performance for estimating the goal features increased by about 25\%.
+This can be attributed to the time complexity of $O(n^2) or O(n^3)$ where n is the number of dimensions.
+
+With the addition of predicted HOMO/LUMO/Band Gap energies for the decay feature vector, the performance for estimating the goal features increased by about 25\%.
+The performance improvement is mostly attributed to the linear reaction between the three values.
 
@@
 So perhaps, if the same tests were done with only heterogeneous side chains adding the correction factor might decrease the total error.
+
+In the results there is a large increase in the performance of the linear models (linear regression and linear ridge regression) when using the decay vector with predictions.
+This can be largely accounted for the linear relation between the HOMO, the LUMO, and the Band Gap energy levels $$BandGap \approx 0.93 (LUMO - HOMO) - 0.15$$.
 
@@
 Calculating the same properties using these machine learning methods took about 4 seconds for each property for all 1100 structures.
-Because of the way that machine learning algorithms work, the majority of the time spent for each of these calculations is spent in the training phase; fortunately, this calculation is only required once so by .
+Because of the way that machine learning algorithms work, the majority of the time spent for each of these calculations is spent in the training phase; fortunately, this calculation is only required once so by pre-trainting the models the total time required can be greatly reduced.
 Once the models have been trained, these calculations are often reduced to just matrix multiplications leading to it taking just 0.1 seconds to calculate each property for all 1100 structures.
@@
 As an end goal, it would be nice to generalize these machine learning methods such that they could be used for any structure.
-\hl{While the...} but perhaps there is a way to do it based off localized functional groups.
+\hl{The naming scheme described would not generalize to other structures, but perhaps a similar treatment of functional groups would lend itself to similar results.}
 
@@
 This is attributed to inexperience with proper methodologies with Neural Networks.}
+
 \hl{Also, the methods mentioned in }\cite{hansen_assessment_2013} \hl{were tested and the results were not as good as any of the other name based features (0.25-0.35 eV).
-In addition to the accuracy problems, it had severe performance problems because it relys on $O(n^2)$ elements in each feature vector where $n$ is the number of atoms in the structure.
-To save time, only structures with $<45$ atoms total were tested, leaving about 450 structures.}
+In addition to the accuracy problems, it had severe performance problems because it relies on $O(n^2)$ elements in each feature vector where $n$ is the number of atoms in the structure.
+To save time, only structures with $<45$ atoms total were tested, leaving about 450 structures.
+Attempting the full data set is not feasible with all the structures/atoms.
+By using all the structures and using PCA to reduce the dimensionality down from 52,000 to 500 retains 99.97\% of the variability of the data (0.24 $\pm$ 0.04 eV MAE).
+To run the full data set it is expected to take on the order of 10s to 100s of days.
+(plus SVM does not work well when features >> samples)}
+
+\section{Acknowledgments}
+
+\hl{David Yaron, Gregorie Montavon, Bucknell (Marcy), University of North Georgia Department of Chemistry and Biochemistry, ...}
 
@@
 
+\section{Other}
+
+The DFT calculations were done using the computing cluster \hl{Marcy from Bucknell} and Gaussian 09.
+The machine learning algorithms used were the ones implemented in the \hl{Scikit-Learn Python Library}.
+All of the machine learning calculations were done on a single consumer quad core computer.
+
+OTHER
+numpy, scipy, matplotlib
+
 \end{document}

### 2014-08-15 paper/paper.tex
More paper updates

@@
 The method presented in this paper takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations.
-By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for the benzobisazole structures tested.
+By using supervised machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for the benzobisazole structures tested.
 These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculations.
@@
 
-To take on both of both of these problems, we will be looking machine learning methods to both be able to predict molecular properties, but with the goal that these calculations would be inexpensive but retain the same level of accuracy.
+To take on both of both of these problems, we will be looking machine learning methods to both be able to predict molecular properties inexpensively but retain the same level of accuracy as DFT.
 In recent work, various machine learning methods have been shown to be fast ways to predict properties of many systems and specifically, has been shown to be a viable way to predict properties of molecules\cite{hansen_assessment_2013} \cite{montavon_machine_2013}.
@@
 
+\subsection{Coulomb Matrix}
+(Montavon et al.)
+$$
+M_{ij} =
+\begin{cases}
+    0.5 Z_i^{2.4} &: i = j \\
+    \frac{Z_i Z_j}{|R_i - R_j|} &: i \ne j \\
+\end{cases}
+$$
+Specifically, to reduce the dimensionality Principal Component Analysis was used to reduce these vectors from 52,000 elements to 500 elements.
+
+(Take lower triangle and convert the matrix to a vector)
+$$M \rightarrow M_v$$
+$$PCA(M_v) \rightarrow M_{smaller}$$
+
+\hl{Should I add this and include those results?}
+
 \section{Machine Learning Methods}
@@
 The mean value method is used as a baseline for all of the other methods with its interpretation being the error that would be gotten by just guessing.
+The mean value method does not use at the feature vector to make its prediction, so all of the different methods will have the same result for it.
+\hl{Should I add NN?}
 
@@
 The minimum located in the center corresponding to the ideal pair of hyperparameter values to use for the machine learning model.
-Similar scan procedures were done for the hyperparameters of the other models to find the lowest testing error.}
+Similar scan procedures were done for the hyperparameters of the other models to find the lowest testing error.\hl{Relevant?}}
    \label{fig:scan}
@@
 
+ \begin{figure}[H]
+   \begin{center}
+     \includegraphics[width=5in]{figures/overall.pdf}
+   \end{center}
+   \caption{\hl{include something similar?}}
+   \label{fig:scan}
+ \end{figure}
+
 Once all the DFT calculations were completed, the resulting log files were processed for the HOMO, LUMO, and Band Gap energy values.
@@
 Once all the data and feature vectors were collected, they were feed into the machine learning algorithms.
+Specifically, we will be looking at supervised learning, meaning that the methods will be trained on (feature vector, property) pairs and then for the testing they will be given just feature vectors and be expected to estimate the respective property value.
 For each feature vector, property, method set the methods relevant hyperparameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors).
 Then using these optimized hyperparameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds \hl{[CITE]}.
+k-Folds and the cross validation are used to ensure that the final model generated is not biased towards the particular set of data used for training (overfitting).
 All of the results were then tabulated and compared based on their mean absolute errors (MAE) calculated as the distance the ML predicted value was from DFT calculated value.
@@
 This increased speed could especially be seen when training the data.
-This can be attributed to the time complexity of $O(n^2) or O(n^3)$ where n is the number of dimensions.
+\hl{This can be attributed to the time complexity of $O(n^2) or O(n^3)$ where n is the number of dimensions.}
 
@@
 
-\hl{David Yaron, Gregorie Montavon, Bucknell (Marcy), University of North Georgia Department of Chemistry and Biochemistry, ...}
+\hl{David Yaron, Gregorie Montavon, Bucknell (Marcy), XSEDE (Blacklight, Gordon, Trestles), University of North Georgia Department of Chemistry and Biochemistry, ...}
 
@@
 
+All of the code and data for this paper can be found in the following two git repositories.
+
+All of the actual machine learning code:
+
+\url{http://www.github.com/crcollins/ML/}
+
+The code to generate benzobisazole structures/names:
+
+\url{http://www.github.com/crcollins/chemtools-webapp/}
+
 \end{document}

### 2014-09-17 paper/paper.tex
Update paper

@@
 
+In recent years there has been a large interest in the creation of organic solar cells instead in lieu of their inorganic counterparts.
+The main driving reasons for such advancements are because organic solar cells are cheaper to manufacture, and they are also are \"cleaner\".
+\hl{Organic solar cells have been a hot topic in chemistry and material science research...
+much of the work involving permuting many different structures } \hl{150,000, 156,314 cores, 1.21 petaflops Mark Thompson USC}
 There are many different molecule groups that are being looked at for use as organic solar cells \hl{[CITE]}.
-One such group is the benzobisazoles \hl{[CITE]}.
+The structures often are composed of many similar features such as polymeric structures and highly conjugated systems.
+One possible group of structures are the benzobisazoles \hl{[CITE]}.
+In previous work, various benzobisazoles have been shown to have interesting optoelectronic properties, thus making them viable for use as organic solar cells\hl{[CITE]}.
+
 To optimize the optoelectronic properties of molecules for use in solar cells, various electron donating and electron accepting groups are added to the structure to shift electron density.
@@
 \begin{equation}\label{decay2}
-    V = \sum_i^n \left(A \left(\frac{d_i}{M_i}\right)^{-H} \right)^{p}
+    V = \sum_i^n \left[A \left(\frac{d_i}{M_i}\right)^{-H} \right]^{p}
 \end{equation}
@@
 \subsection{Coulomb Matrix}
-(Montavon et al.)
+For the work by Montavon et al, they make use of a feature structure that depends on the atomic number, and the coordinates of each atom in the structure.
+From that, they construct a distance matrix of the following form of which they call the Coulomb Matrix.
+
 $$
@@
 \begin{cases}
-    0.5 Z_i^{2.4} &: i = j \\
-    \frac{Z_i Z_j}{|R_i - R_j|} &: i \ne j \\
+    0.5 Z_i^{2.4} & i = j \\
+    \frac{Z_i Z_j}{|R_i - R_j|} & i \ne j \\
 \end{cases}
@@
 In the results there is a large increase in the performance of the linear models (linear regression and linear ridge regression) when using the decay vector with predictions.
-This can be largely accounted for the linear relation between the HOMO, the LUMO, and the Band Gap energy levels $$BandGap \approx 0.93 (LUMO - HOMO) - 0.15$$.
+This can be largely accounted for the linear relation between the HOMO, the LUMO, and the Band Gap energy levels.
+
+$$BandGap \approx 0.93 (LUMO - HOMO) - 0.15$$
 
@@
 To run the full data set it is expected to take on the order of 10s to 100s of days.
-(plus SVM does not work well when features >> samples)}
+(plus SVM does not work well when $N_{features} >> N_{samples}$)}
 
@@
 
-\hl{David Yaron, Gregorie Montavon, Bucknell (Marcy), XSEDE (Blacklight, Gordon, Trestles), University of North Georgia Department of Chemistry and Biochemistry, ...}
+\hl{David Yaron, Gregorie Montavon, Bucknell (Marcy), XSEDE (Blacklight, Gordon, Trestles), University of North Georgia Department of Chemistry and Biochemistry, Carnegie Mellon Department of Chemistry, ...}
 
@@
 
-OTHER
 numpy, scipy, matplotlib
@@
 
-All of the actual machine learning code:
+All of the machine learning code:
 

### 2014-11-22 paper/paper.tex
Update paper
Add a small update to the paper

@@
 This matches similarly to the results seen in \hl{....
-[CITE]}; however, they found that the Laplacian kernel performed the best.
+[CITE]}\cite{hansen_assessment_2013}; however, they found that the Laplacian kernel performed the best.
 The suspected reason for the difference in the two results is thought to be because the method used in that study involved single atoms as features, whereas this method was dealing with entire functional groups.
@@
 \hl{The naming scheme described would not generalize to other structures, but perhaps a similar treatment of functional groups would lend itself to similar results.}
+
+Upon doing PCA on the binary feature vectors, it can be seen that the weights/influence for each of the substituents is directly related to its Hammet parameter value.
 
